\documentclass[char]{guildcamp2}
\begin{document}

\name{\cBabyFae{}}

Most monsters and humans underestimate the fae. They assume that just because you are fun-seeking, capricious, and whimsical when the situation allows it, that you cannot possibly rise to the occasion when the situation turns serious. You know from your centuries of experience that many such monsters who have underestimated and looked down upon the fae are now lost to the history books. The fae have been around a very, very long time and behind their whimsical nature is an ability to adapt to changing environments that allows you to survive in situations that have crushed countless ``more powerful'' monsters who tried to resist with strength alone. As the leader of the Winter Court, you embody this spirit of adaptability, and this war council is a testament to the changing times. You will have to use your considerable cunning to see to it that whatever happens here, the fae come out on top.

Although you lead the Winter Court and your partner \cTreeFae{\intro} leads the Summer Court, on matters of fae history you both defer to the eldest fae, The Oracle. Last night, she summoned the two of you to an omnious meeting. At this meeting, she spoke in ringing tones of the alignment of stars and prophesied the rising of Ezekiel, the King who will unite all fae folk, old and young, Summer and Winter alike.  She impressed upon you and \cTreeFae{} the importance of cooperation in performing the ritual to raise him. It must be done using a gem from the Tomb of Ezekiel, whose location was lost long long ago.  However, she has sensed that one of the jewels will be at the council meeting the ancient dragon \cOnyx{\intro} is holding to coordinate action against humans.  The Oracle then gave you the Tome of Ezekiel, which describes the elaborate ritual you must perform.  You and \cTreeFae{} swore to her that you would not fail. You find \cTreeFae{} and \cTreeFae{\their} fellow Summer fae to be a bit too obsessed with their forests, but for a matter important enough for the Oracle to summon you, you're willing to tolerate \cTreeFae{\them} for a while.

Your passion is for dreams. In real life (except for fae) both monsters and humans are honestly quite boring. They act under a mountain of inhibitions that prevent them from acting the way they want. Dreams are the exact opposite. In dreams, people are so much more exciting. You crave the vast range of emotions present in dreams, from euphoria to carnal savagery, and always seek to cultivate intensity of emotion in others. Still, you rarely get to interact with races besides other fae and the monsters such as basilisks that live in the caves and mountains you call home. However, this council will have many races, such as vampires and minotaurs, that almost never interact with fae. You fully intend to take the opportunity to explore their dreams by whatever means necessary. Unbeknownst to many outside the fae, dreams offer more than just insight into someone's emotional turmoil: with the right preparation they can control and subvert another's mind.

The fae of the Winter Court live alongside several monster races, but the only such race present at this War Council is the basilisks, represented by \cBasilisk{\intro}. You two get along as well as can be expected, and you will hopefully look after each other's interests here. \cTreeFae{} does not like \cBasilisk{} and is far too close with \cEnt{\intro}. \cEnt{\intro} does not even have dreams as far as you can tell, and worse yet, \cEnt{\intro} wants to turn humans into trees. You are happy for there to be conflict with humans, but if they are trees (or stones) they will not dream and are useless to you. You will have to deter \cTreeFae{} from helping this annoying ent or otherwise stall the ent's plans. You are also a bit wary of the djinni \cWizard{}, who \cTreeFae{} seems to be infatuated with. You are too capricious to really care, but there's something about \cWizard{} that bears a bit closer attention. You can't be sure yet, but you think this djinni might be enscrolling \cTreeFae{}.

\cOnyx{} is naturally going to insist that you deploy your forces in this war against the humans. Although monsters do sort of dream, humans have \emph{by far} the tastiest of all dreams and an emotional richness that far outweighs their diminutive forms. You really do not want the humans to be crushed: you know that the monster horde will push forward and given how frail humans are, you fear that your supply of dreams will run dry. Still, you also don't want your people to be killed or hurt. You are fine with other's sacrificing themselves though, as you'd certainly stand to benefit if races like the trolls and demons are wounded a bit in the battle. You would have to be given some pretty significant incentives to actually commit your forces: the fae are really not a combat-oriented race. And under no circumstances would you deploy your troops unless \cTreeFae{} did so as well. On the other hand, if you manage to bring Ezekiel back, the fate of the fae may change rapidly and you would likely listen to his advice.

While you're pursuing all these goals, you also have to worry about others trying to steal your magic.  Fae magic is renowned for power (it can cure ugliness, for one thing), and you wouldn't be surprised if someone here wants it.

You've also heard about some rumors of surrendering to the humans, but you don't really know what to think about that yet. Like everything at this council, you'll just have to figure out more and adapt as needed. 

\begin{itemz}[Goals]
  \item Raise Ezekiel so he can unite all fae folk.
  \item Make sure the Winter Court fae come out ahead of the other races on any war negotiations. Keeping your people safe is of utmost importance to you.
  \item Play with the dreams of the other monsters present at the council.
  \item Help \cBasilisk{}, as long as it's not too much trouble.
  \item Stop \cEnt{\intro} from turning humans into trees.
  \item Make sure no one steals your fae magic.
  \item Try to avoid letting the humans get utterly crushed by the monster army.
\end{itemz}


\begin{contacts}
  \contact{\cOnyx{}} An ancient dragon who called this council meeting.
  \contact{\cTreeFae{}} Your counterpart from the Summer Court, with whom you have an uneasy alliance.
  \contact{\cBasilisk{}} The leader of the basilisks who lives near the caves where the Winter Court fae live.
    \contact{\cEnt{\intro}} An ent who wants to turn everyone into trees.
        \contact{\cWizard{}} A djinni who \cTreeFae{} is infatuated with.
\end{contacts}

\end{document}
