\documentclass[char]{guildcamp2}
\begin{document}

\name{\cBasilisk{}}

Unlike many of your fellow magical beings, you \emph{like} humans.  You think they're great.  They're so slow and bumbling, so clumsy as they try to run across the mountainous terrain.  They trip over rocks and fall over bushes and lie there panting and sobbing as you glide up to them.  Some of them start begging.  All of them squinch their eyes shut as you gaze at them for long moments and listen to their pounding hearts.  It's a waiting game, and they always crack first.  Hearing no sounds, eventually they open their eyes for a peek -- and see you, just a few feet away, patient and still.  Then the inevitable shriek of fear, the scramble to get to their feet, and off they bound again.  You repeat this until they're exhausted and begging at your, well, not feet.  At your mercy.  Depending on your mood, sometimes you turn your Petrifying glare on them and transform them into stone.  Sometimes you toy with them a little longer, not switching on your glare yet, until they begin to hope that the stories about basilisks are false.  And \emph{then} you Petrify them.  Ah, bliss.  You're never quite so happy as you are at the end of a chase, when you admire your newest statue.

Until your ability began to fail you.  It was such a gradual process that it took a while for you to realize that you were no longer Petrifying things permanently.  The duration has been steadily decreasing.  At first, you tried to make the best of it.  You convinced yourself that it just adds to the game.  The humans wake, realize that they're still alive, and you can toy with them some more before killing their hope again.  But now the Petrification only lasts five minutes!  It is unbearable.  Your main joy in life has been taken from you.  

And even worse, you achieved your position as leader of all basilisks because of your prowess in these games.  In terms of psychological torture, you are still peerless among your kind and retain their respect, but how long before some young whippersnapper challenges you?  You \emph{must} find a way to heal your glare.  Luckily, the ancient dragon \cOnyx{\intro} has summoned leaders of all the magical creatures for a council meeting to discuss how to deal with the human horde.  You're sure that someone here will know how to cure you.

It does mean you're going to have to mingle with the others, which you normally avoid as much as possible.  Although you hide it beneath a crusty exterior, you're actually very sensitive and unhappy.  You look like a dragon but can't fly.  You look like a snake but have no poisonous fangs.  You don't have legs, so you're treated like an animal rather than a thinking being.  Now that your Petrifying glare has begun to fail, you don't even have an awesome power, as the Summer Court fae, \cTreeFae{\intro}, likes to remind you.  Even a pathetically weak fae is mocking you!  No one respects you!  All you have left is your beautiful emerald hide.  You \emph{have} to find a way to fix your glare so they fear you.

But they do need something from you.  They want you to commit your basilisk army to the battle against the humans.  So a basilisk is something to be ridiculed until it is useful?  Anger fills you at the thought.  Yet in this struggle, you see an opportunity.  Let the other magical creatures and the humans fight and die.  If you can keep your own army out of the fight, you'll be in a strong position to conquer the other magical creatures' lands afterwards, and enslave the remaining humans to be your playthings.  Unless the Winter Court fae, \cBabyFae{\intro}, convinces you to deploy your troops.  \cBabyFae{\They} is the closest thing to a friend you have, and you have an unfortunate soft spot for \cBabyFae{\them}. The only problem with \cBabyFae{} is that they are often hanging around the insulting \cTreeFae{}; you will have to find a way to separate them. You also have occasionally learned a bit about chasing humans from the minotaur, \cMinotaur{}. \cMinotaur{} is not a friend, per-se, but \cMinotaur{\they} is very good at tormenting humans in stone mazes, not entirely unlike the tree mazes you employ.

You've only been here for a few minutes, but already in your exploration of the castle, you've seen hints that someone is working to build golem.  Inspiration struck you -- you could build yourself a pair of mechanical legs!  Then you'll be humanoid in form!  You make a mental note to figure out who's making golems.  Maybe he or she will help you.  If that plan fails, it might be possible to create shape-shifting legs using fae magic.  You'd never steal fae magic from \cBabyFae{}, but \cTreeFae{} is certainly fair game.

All in all, this will be a profitable meeting for you!


\begin{itemz}[Goals]
  \item Create a potion to fix your Petrify glare.
  \item Obtain legs, either by building golem legs or by using fae magic if necessary.
  \item Enslave humanity (they make wonderful playthings).
  \item Keep your own army out of the fight if possible.
  \item Separate \cBabyFae{} and \cTreeFae{}.
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cOnyx{}} An ancient dragon who summoned everyone to this council meeting.
  \contact{\cBabyFae{}} A Winter Court fae who lives nearby, perhaps the closest thing to a friend you have.
  \contact{\cTreeFae{}} A Summer Court fae who makes fun of you.
  \contact{\cMinotaur{}} A minotaur talented at tormenting humans in stone labyrinths.
\end{contacts}


\end{document}
