\documentclass[char]{guildcamp2}
\begin{document}

\name{\cCleric{}}

\cenquote{This is a war universe. War all the time. That is its nature.-William S. Burroughs}

You are a human cleric of the God of War, Groznak. After ambushing and killing the ogre delegation, you've arrived at this council of monsters disguised as an Ogre with one goal: Summon your god and kill everyone. You can't wait to see the floors of this castle painted red with blood, the walls smeared with entrails, and the screams of the dying echoing down the corridors once you summon your god. 

However, the rest of your compatriots failed to teleport into this castle thanks to those accursed wards, so you're the only cleric of the god of war here. This is a problem as you need help to cast the summoning ritual. Also, without any backup, you know that if you're exposed as a human you will be swiftly killed by all the monsters here. After all, it is a council about going to war with the humans. You may crave death and destruction, but it is no fun if you are not around to witness it because you got yourself killed. To make matters worse, you seem to have misplaced a crucial piece to the ritual: your Holy Book. In order to perform the ritual, you have to find that book first.
		
Still, you are nothing if not optimistic. You already have a solution to the problem that the ritual requires multiple participants. This is a council of war, and you worship the god of war. Surely some creatures here could be convinced to help you with your ritual. Monsters are stupid enough that they would probably fall for any old lie you told them. Of course, you expect that once Groznak is summoned, the monsters will attempt to flee the castle. If you can sabotage the teleportation runes ahead of time, you can prevent everyone from leaving, turning the castle into a death trap. Delightful.
	
While you work on recruiting followers you'll need to maintain your disguise. Stay safe; try to act like you think an Ogre would. Hopefully none of the monsters here knew the Ogre you are disguised as. If you are revealed, you do have a secret weapon with you -- a gun. The gun is a new development by the artificers in your kingdom. Do try to keep it a secret unless absolutely necessary as revealing you have it will almost certainly blow your cover, and you can't fight your way out of all of these monsters.

All told, this would be easier with allies. In the short time you've been here, you heard the minotaur mention something called the ``Power Society.'' That sounds like a promising start. You should investigate. Luckily, being a cleric of the god of war grants some perks. You have the ability to grant one army the chance to back stab another army that has been deployed against the humans. Since monsters are notoriously incapable of cooperating with each other, this should prove a powerful bargaining chip in gaining allies.

Speaking of deploying armies against the humans, you frankly can't think of anything more delightful than an evenly matched battle that leads to endless chaos and bloodshed, monster and human alike. Nothing pleases you and your god more than death. What a glorious day for Groznak if you could manipulate the monsters into fielding a united force approximately equal to the human armies.

\begin{itemz}[Goals]
	\item Summon Groznak, the God of War.
	\item Ensure that the monster army matches the human army in strength.
	\item Sabotage the teleportation runes so no one can escape.
	\item Join the Power Society.
  \item Keep your disguise up.
\end{itemz}

\begin{itemz}[Notes]
\item As a cleric of the God of War, you may pick up his Holy Book (\iHolyBook{}) and Sacrificial Dagger {\iDagger{}). You have been properly ordained, and thus the wards that prevent them from being picked up by other creatures do not affect you.
\end{itemz}

\begin{contacts}
	\contact{\cMinotaur{}} You overheard \cMinotaur{\them} mention something called the ``Power Society.''
\end{contacts}


\end{document}
