\documentclass[char]{guildcamp2}
\begin{document}

\name{\cDemon{}}

\cenquote{``His twisted words entice the weak.\\The price is paid.\\The power is mine!''}{-- Ravenous Demon, Archdemon of Greed}

You are the leader of the abyss. You thrive on the chaos around you and encourage it on every level. The great \cOnyx{} has summoned you to this place to discuss the fate of monsters versus humans —- the truth is that you don’t really care. You and your kind can make deals with humans just as well as you can make deals with monsters. You do love that the monsters are all in a tizzy about this whole ``gun'' device the humans have crafted. While everyone is all running about like a headless kobold, you are sitting back and chuckling at their screams; when things get hairy all you have to do is blink into the Abyss. (Although, as long as you are in \cOnyx{}'s castle, you can't blink out completely and return to the Abyss. \emph{As a game kludge, game space is closed and you cannot leave the castle.})

You have made it your goal to get as involved in everyone's lives as possible; you absolutely love the rush you feel when you have pulled the wool over someone’s eyes or have manipulated them into throwing their livelihoods away for a few pennies. You keep a tight network of demons, devils, ghosts, and other monsters that deal in information and subterfuge. As the leader of the demons, you know the value in loyal informants who bring you timely, accurate information. As such, you know little tidbits about everyone here; you need to be aware of potential military invasion as well as knowing how you can sneak your way into hearing more rumors. In your book, treasures are only topped by gossip and gossip is only topped by using that gossip to anonymously sabotage people's plans.

In addition to information, you barter in treasures, and of course, souls. You are one of the few demons with knowledge of the more obscure magicks and guarantee the absolute top quality in supplies. As is traditional of a demon of your stature, you can always make a deal for someone's soul; assuming they have one. If you are dealing with someone with no soul to give and no interest in magic, you can always make them hunt down a new legendary sword for your legendary sword collection. 

Upon receiving the letter from \cOnyx{} the Great Black Dragon, you quickly determined who might be there at that soirée and what you might tempt them with: \cSphinx{} will undoubtedly be there. You also think that \cRed{} and \cVampire{\full} should be there, as leaders of the two oldest monster organizations in Astyria. Even the lowly Goblin leader will likely be in attendance. You pack some things they may like; a quill for that troll poet, a lovely emerald necklace for that tree fae\ldots{} You rub your hands together. This should be fun. Monsters are always full of ulterior motives and you always love to manipulate them!

Everyone always wants something. It is just a matter of identifying what. Your skill at doing just that has elevated you to leader of the demons. You never miss a chance to offer a deal to someone, and you always haggle mercilessly. Everyone knows you, but not everyone loves you -- in fact, most monsters and humans you interact with despise you, but they always come back for more obscure knowledge or artifacts! After all, you are the best.

While demons don't hoard things the same way that dragons do, you do have a soft spot for swords. You know that stuffy old black dragon has a beautiful masterpiece, the \iSwordofIce{}, in \cOnyx{\their} possession; if only you could come up with something \cOnyx{\they} wants, it would be yours! In addition, you have been searching for the missing pieces of the \iRVorpal{} for centuries now and you have reason to suspect that that scaly, old churl has a fragment somewhere. One of your dimwitted imps was able to convey that one of the other council members holds a second fragment, but you were unable to understand where. You incinerated the imp on the spot for his incompetence. 

One of your other imps was mildly more useful. He mentioned something about rituals. Well of course someone here was going to try a ritual. After all, What would an unprecedented gathering of monsters be without someone attempting a ridiculously reckless, large scale magical ritual? The specifics of rituals have never interested you, but their generalities certainly don't escape you. Any ritual you can think of will require a \iRitualWand{}, a magical item of incredible rarity that must be consumed during a ritual. You suspect no more than 3 exist in the world, and you know where two of them are. By process of elimination, only one could possibly be present in \cOnyx{}'s castle. It will be delightful to watch the monsters fighting for control of the wand. And would be even more delightful if you could get your hands on it first, and enjoy the bidding war that ensues.

You grab your satchel. ``Goodbye, my imps! I must away and help decide the fate of the humans!'' you shout to no one in particular. ``You're in charge,'' you casually say as you pass a statue of yourself and get ready to teleport to \cOnyx{}'s castle.


\begin{itemz}[Goals]
  \item Extract as much information and as many valuable items as possible from the other delegates. You have plenty of both, but it is always good to have more.
  \item Join as many factions as possible.
  \item Cause and encourage chaos whenever possible.
  \item Make deals to trade away your information and items that people want. Ensure that the deals are as outrageously favorable to you as possible, ideally subtly screwing over the other party in the process.
  %\item Find out who the human is! It will surely cause chaos.
  \item Find and claim legendary swords to add to your collection, including the \iSwordofIce{} and the missing pieces of the ``\iVorpalSwordofWonder{\MYname}'' (\iVorpalSwordofWonder{\MYnumber})
  \item Disrupt any attempt at a final decision at the meeting.
\end{itemz}

\begin{contacts}
  \contact{\cOnyx{}} The elder dragon leading the council.
  \contact{\cVampire{}} A powerful vampire rivaling with \cLich{}. Also leader of the Loremasters. Your information suggests that \cVampire{\they} wants to find a way to walk under the sun unharmed. You suspect the Fae are the answer. Their magics are all too often the answer. 
  \contact{\cLich{}} Once a powerful human sorcerer, now an even more powerful lich. He is always looking for more power, and to to that end is a member of the Power Society.
	\contact{\cTreeFae{}} A fae thoroughly infatuated with nature. Capricious and fickle, \cTreeFae{\they} is never boring.
	\contact{\cBabyFae{}} A fae thoroughly infatuated with drinking the dreams of human babies. You appreciate the mischievousness of the fae.
	\contact{\cTroll{}} A troll. \cTroll{\They} seems to have some intense belief that \cTroll{\they} has a talent for poetry. You disagree but find it highly amusing how much the status quo is disrupted by \cTroll{\their} antics.
	\contact{\cWizard{}} You never paid too much attention to the leader of the Djinni because \cWizard{\they} never seems to want to participate in your deals. \cWizard{\they} probably begrudges the “competition” with \cWizard{\their} wish granting. What a shame!
	\contact{\cCleric{}} You heard that the Ogre horde had been swarmed by humans but apparently they are hardier than they look! An impressive feat!
	\contact{\cBasilisk{}} You heard that the Basilisk's stone gaze is weakening for some unknown reason. How bizarre. Perhaps you could render some assistance? For the appropriate price, of course.
	\contact{\cMinotaur{}} The minotaur. \cMinotaur{\Their} manner of speak reminds you of your imp minions back home. How quaint. You know of a longstanding intellectual rivalry between \cMinotaur{\they} and \cSphinx{}.
	\contact{\cSphinx{}} Speaking of \cSphinx{}, you always were amused by \cSphinx{}'s ability to play with the minds of others. You love chaos, but you can't stand the cryptic sentences from \cSphinx{\them}; you keep your distance but with sincere respect.
	\contact{\cGoblin{}} This plucky little goblin wants to rule the world someday! You have no faith that \cGoblin{} will succeed in this endeavor, but if you can convince \cGoblin{\them} to trade away all of \cGoblin{\their} life savings, or better yet his very soul, for the cause you will.
	\contact{\cEnt{}} The Ent is the oldest and wisest of his forest. He is known for having disdain for undead but seems to be generally peaceful. You happen to know that he has a deep, personal grudge against the lich and \cRed{} because they burned down his forest.
\end{contacts}

\end{document}








%\documentclass[char]{guildcamp2}
%\begin{document}
%
%\name{\cDemon{}}
%
%\cenquote{``His twisted words entice the weak.\\The price is paid.\\The power is mine!''}{-- Ravenous Demon, Archdemon of Greed}
%
%You are the leader of the abyss. You thrive on the chaos around you and encourage it on every level. The great \cOnyx{} has summoned you to this place to discuss the fate of monsters versus humans—-the truth is that you don’t really care. You and your kind can make deals with humans just as well as you can make deals with monsters. You do love that the monsters are all in a tizzy about this whole ``gun'' device the humans have crafted. While everyone is all running about like a headless kobold, you are sitting back and chuckling at their screams; when things get hairy all you have to do is blink into the Abyss. (Although, as long as you are in \cOnyx{}'s castle, you can't blink out completely and return to the Abyss. \emph{As a game kludge, game space is closed and you cannot leave the castle.})
%
%You have made it your goal to get as involved in everyone's lives as possible; you absolutely love the rush you feel when you have pulled the wool over someone’s eyes or have manipulated them into throwing their livelihoods away for a few pennies. You keep a tight network of demons, devils, ghosts, and other monsters that deal in information and subterfuge. As the leader of the demons, you know the value in loyal informants who bring you timely, accurate information. As such, you know little tidbits about everyone here; you need to be aware of potential military invasion as well as knowing how you can sneak your way into hearing more rumors. In your book, treasures are only topped by gossip and gossip is only topped by using that gossip to anonymously sabotage people's plans.
%
%In addition to information, you barter in treasures, and of course, souls. You are one of the few demons with knowledge of the more obscure magicks and guarantee the absolute top quality in supplies. As is traditional of a demon of your stature, you can always make a deal for someone's soul; assuming they have one. If you are dealing with someone with no soul to give and no interest in magic, you can always make them hunt down a new legendary sword for your legendary sword collection. 
%
%Upon receiving the letter from \cOnyx{} the Great Black Dragon, you quickly determined who might be there at that soirée and what you might tempt them with: \cSphinx{} will undoubtedly be there. You also think that \cRed{} and \cVampire{\full} should be there, as leaders of the two oldest monster organizations in Astyria. Even the lowly Goblin leader will likely be in attendance. You pack some things they may like; a quill for that troll poet, a lovely emerald necklace for that tree fae\ldots{} You rub your hands together. This should be fun. Monsters are always full of ulterior motives and you always love to manipulate them!
%
%Everyone always wants something. It is just a matter of identifying what. Your skill at doing just that has elevated you to leader of the demons. You never miss a chance to offer a deal to someone, and you always haggle mercilessly. Everyone knows you, but not everyone loves you -- in fact, most monsters and humans you interact with dislike you, but they always come back for more obscure knowledge or artifacts! After all, you are the best.
%
%While demons don't horde things the same way that dragons do, you do have a soft spot for Swords. You know that stuffy old black dragon has a beautiful masterpiece, the \iSwordofIce{}, in \cOnyx{\their} possession but if only you could come up with something \cOnyx{\they} wants, it would be yours! In addition, you have been searching for the missing pieces of the \iRVorpal{} for centuries now and you have reason to suspect that the scaly grump has a fragment somewhere. One of your dimwitted imps was able to convey that one of the other council members holds a second fragment, but you were unable to understand where. You incinerated the imp on the spot for his incompetence. 
%
%You grab your pack. ``Goodbye, my imps! I must away and help decide the fate of the humans!'' you shout to no one in particular. ``You're in charge,'' you casually say as you pass a statue of yourself and get ready to teleport to \cOnyx{}'s castle.
%
%
%
%\begin{itemz}[Goals]
%  \item Extract as much information and as many valuable items as possible from the other delegates. You have plenty of both, but it is always good to have more.
%  \item Join as many factions as possible.
%  \item Cause and encourage chaos whenever possible.
%  \item Make trades and deals to exchange your information and items that people want. Ensure that the deals are as favorable to you as possible.
%  %\item Find out who the human is! It will surely cause chaos.
%  \item Find the missing pieces of the ``\iVorpalSwordofWonder{\MYname}'' (\iVorpalSwordofWonder{\MYnumber})
%  \item Disrupt any attempt at a final decision at the meeting.
%\end{itemz}
%
%\begin{contacts}
%  \contact{\cOnyx{}} The elder dragon leading the council.
%  \contact{\cVampire{}} A powerful vampire rivaling with \cLich{}. Your information suggests that \cVampire{\they} wants to find a way to walk under the sun unharmed. You suspect the Fae are the answer. Their magics are all to often the answer.
%  \contact{\cLich{}} Once a powerful human sorcerer, now an even more powerful lich. He is always looking for more power.
%	\contact{\cTreeFae{}} A fae thoroughly infatuated with nature. Capricious and fickle, \cTreeFae{\they} is never boring.
%	\contact{\cBabyFae{}} A fae thoroughly infatuated with drinking the dreams of human babies. You appreciate the mischievousness of the fae.
%	\contact{\cTroll{}} A troll. \cTroll{\They} seems to have some intense belief that \cTroll{\they} has a talent for poetry. You disagree but find it highly amusing how much the status quo is disrupted by \cTroll{\their} antics.
%	\contact{\cWizard{}} You never paid too much attention to the leader of the Djinni because \cWizard{\they} never seem to want to participate in your deals. What a shame!
%	\contact{\cCleric{}} You heard that the Ogre hoard had been swarmed by humans but apparently they are hardier than they look! An impressive feat!
%	\contact{\cBasilisk{}} You heard that the Basilisk's stone gaze is weakening for some unknown reason. How bizarre. Perhaps you could render some assistance? For the appropriate price of course.
%	\contact{\cMinotaur{}} The minotaur. \cMinotaur{\Their} manner of speak reminds you of your imp minions back home. How quaint. You know of a longstanding intellectual rivalry between \cMinotaur{\they} and \cSphinx{}.
%	\contact{\cSphinx{}} Speaking of \cSphinx{}, you always were amused by \cSphinx{}'s ability to play with the minds of others. You love chaos, but you can't stand the cryptic sentences from \cSphinx{\them}; you keep your distance but with sincere respect.
%	\contact{\cGoblin{}} This plucky little goblin wants to rule the world someday! You have no faith that \cGoblin{} will succeed in this endeavor, but if you can convince  \cGoblin{\them} to trade away all of \cGoblin{\their} life savings for the cause you will.
%	\contact{\cEnt{}} The Ent is the oldest and wisest of his forest. He is known for having disdain for undead but seems to be generally peaceful.
%\end{contacts}
%
%\end{document}
