\documentclass[green]{guildcamp2}
\begin{document}
\name{\gEndgame{}}

\section{End Game scenarios}

\section{The Dice Roll-skip if peace is chosen}
\begin{enum}
	\item 1. If the monsters lose the dice roll by more than 4: Your armies are crushed by the overwhelming forces of the humans. The end seems near for the monster species of Astyria.
	\item 2. If the monsters lose the dice roll by 4 or less: Although they fought valiantly, your forces were defeated by the human army. It will be a long, bloody struggle to retain your existence.
	\item 3. If the monsters tie with the dice roll: Your armies stalemate with the human army. The status quo is maintained. The future is yet to be seen if the monsters of Asyria will remain a powerful force in the world.
	\item 4. If the monsters win the dice roll by 5 or less: After a long, bloody fight, your forces emerge victorious. You have successfully pushed back the human menace, and are ready to start the reconquest of human lands.
	\item 5. If the monsters win the dice roll by 6 or more: Your forces sweep aside the human army in a tremendous victory. Already your forces have made great gains in their conquest of the human lands.
\end{enum}

\section {Rituals}
\begin{enum}
	\item 1. If no rituals are performed, nothing happens.
	\item 2. If the kill ritual goes off: Massive amounts of humans start dying rom an unknown cause.
	\item 3. If the domination ritual goes off: A large number of humans shuffle off in a zombie like state towards the monster's territories. (If item 1. or 2. or peace in the previous section happens,) They are quickly found by human forces and return to normal. (If item 3. in the previous section happens,) Some eventually return home, but some are never seen again, rumored to be slaves in various monster kingdoms. (If item 4. or 5. in the previous section happens,) A short while later, there is a massive surge in the number of human slaves in the monster capital.
	\item 4. If the tree ritual goes off: A large number of humans walk off into the nearest forest. Seemingly overnight, these forests double, triple, and even quadruple in size, even to the point where they start to encroach on human towns.
\end{enum}
\section {Supreme Leader-Only read if items 4. or 5. in the first section happen-don't read if peace happens}
\begin{enum}
	\item 1. If Onyx is the Supreme leader: Led by the massive, wise black dragon, the combined forces of the monsters work together to defeat the human army in a tactical display of brillance.
	\item 2. If Lich is the Supreme leader: Led by the ancient lich, the monster army is bolstered by the re-animated corpses of their fallen enemies.
	\item 3. If Ruby is the Supreme leader: Led by the vicious red dragon, the monster army's ferocity in the battle becomes legendary.
	\item 4. If the vampire is the Supreme leader: Led by the Vampire, the monster army takes many human slaves during it's drive into human territory
	\item 5. If none of the above are true, don't read anything
	\end{enum}
\section {If the God of War is summoned}
	\begin{enum}
		\item 1. If item 1. or 2. in the first section happen: Although victorious, the human army, inspired by the blood lust of Groznak, turns on itself. Soon, the entire continent is embroiled in a bloody civil war between human nations.
		\item 2. If item 3. or peace in the fist section happen: Groznak's summoning inspires the armies to fight to the last man. At the end of the battle, not a single monster or human are left standing, and their respective nations soon turn on each other. The entire continent becomes awash in humans' and monsters' blood alike.
		\item 3. If item 4. or 5. in the first section happen: Although victorious, the monster army, inspired by the blood lust of Groznak, turns on itself. Soon, the entire continent is embroiled in a bloody civil war amongst the monster nations.
		\end{enum}
\section {Peace-skip if no one sues for peace}
		\begin{enum}
		\item 0. If the God of War is summoned: Groznak declares that there can be no peace. Only war. All nations that sued of peace are awash in the entrails of their citizens.
		\item 1. If all monster nations get peace: With the end of hostilities between humans and monsters, Astyria enters a golden age. Harmony, understanding, sympathy, and trust abound. 
		\item 2. If item 1. or 2. in the first section happens and the wizard lives: While the human armies triumph over the monster alliance, the monster nations that succesfully sue for peace are welcomed by the humans. Trade flourishes, and both the peaceful monster nations and the humans improve their quality of life.
		\item 3. If item 1. or 2. in the fist section happens and the wizard dies: While the human armies triumph over the monster alliance, the monster nations that succesfully sue for peace are at best treated coldly by the humans. Without a diplomat to vouch for them, tensions mount between the humans and the peaceful monster nations.
		\item 4. If item 3. happens and the wizard lives: The monster nations that succesfully sue for peace are welcomed by the humans. Trade flourishes, and both the peaceful monster nations and the humans improve their quality of life.
		\item 5. If item 3. happens and the wizard dies: The monster nations that succesfully sue for peace are at best treated coldly by the humans. Without a diplomat to vouch for them, tensions mount between the humans and the peaceful monster nations.
		\item 6. If item 4. or 5. happens, the monster nations that sued for peace are considered traitors by the succesful monster alliance. They are invaded in addition to the human lands.
		\end{enum}
\end{document}
