\documentclass[char]{guildcamp2}
\begin{document}

\name{\cEnt{}}

%% This sort of use of \updatemacro is covered in
%% Extras/README-namemappings.


%% quote examples
\bigquote{``For it is easier to shout 'Stop', than to do it''}{The Lord of the Rings: the Two Towers}

You are strong or at least stronger than most. . . you are old. . . or at least older than most. . . it is hard to remember how old you are. . . you have been alive so long. . . all the other races use so many words. . . words are hard. . . but not as hard as your hate. . . they think your people slow. . . calm. . . peaceful. . . but they do not understand. . . nature is just as much wrath and hunger as quiet beauty. . . and you are all wrath. . . They burned your forest. . . \cRed{} the dragon and \cLich{}. . . you will have vengeance. . . you know of a sword rumored to be able to slay the dragon. . . the phylactery of \cLich{} is hidden but you will find it. . . nature always finds a way. . .  but the forest is weakening. . . it needs strength. . . seeds. . . seeds of the world tree. . . you must give them to the delegates to plant. . . but it will not be enough. . . drastic action is needed. . . a ritual to turn the humans into nature. . . man to tree. . . life to life. . . not alone in this true quest. . . \cTreeFae{} and \cTroll{} stand with you. . . they see. . . nature fills them. . . why is unimportant all that matters is the goal. . . they understand nature's value. . . that old dragon called you here about a war. . . \cOnyx{} is so insistent. . . but the war is unimportant compared to nature. . . a blink of the eye. . . whatever plans has the highest chance of helping your people survive. . . helping nature survive... that is wise. . . survival is needed. . . the forest depends on you. . . the time of the tree has come. . .

\begin{itemz}[Goals]
  \item You must get the other war leaders to take the seeds (\iSeedoftheWorldTree{}) and plant them.
  \item Kill \cRed{}.
	\item Kill \cLich{}.
  \item Complete the ritual to turn people into trees.
	\item Discuss the plight of the forest with as many people as possible.
\end{itemz}

\begin{itemz}[Notes]
  \item You are willing to go to war if it will help your people's chance of survival 
  \item You need to find \iSwordofIce{} to kill the dragon
	\item You need to find and destroy the \iPhylactery{} to kill Lich.
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cTreeFae{}} \cTreeFae{\They} said \cTreeFae{\they} would help you turn all humans into trees
  \contact{\cTroll{}} \cTroll{\They} said \cTroll{\they} would help you turn all humans into trees
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.

\end{document}
