\documentclass[char]{guildcamp2}
\begin{document}

\name{\cGoblin{}}



%% quote examples
\bigquote{``Goblins don't care who they catch, as long as it is done smart and secret, and the prisoners are not able to defend themselves''}{-- The Hobbit}

They think you small and unimportant, you will show them. You are important! You are the most important because you are the smartest, fastest, strongest badass there is. Well maybe not strongest, but who wants to be a large muscle bound idiot anyway. You will not need to be a big when you get enough magic power or technological power -- any power would actually do, to show the other races that goblin are the best. In that regard you got plans, plans to get stronger and more powerful.  Not that you need it you are already the most powerful goblin, though everyone laughs when you tell them -- you just need more power so you can actually show the other races why they should fear the goblins. 

Your first plan is golems, why be big when you can have big monsters to hit other big idiots for you. Your spies tell you \cOnyx{} was interested in golems also. But in the end they will be yours, not that you can't use the big idiot.

If the golems fails \cOnyx{} can help you out again, the Lore Masters society told you, because you are best that the old dragon has got some really powerful orb and you want it. They wanted to study it. It has to be good right? They entrusted you to go get it for them, trusting a goblin, a perfect example of why everyone else is dumb. You should probably keep it when you find it as a reward, that seems fair and if the other Lore Masters have anything to say about it then you can always use the orb on them. \cOnyx{}'s treasure room seems like a promising start, but first you need a key.  

But your plans do not end there, oh no. You hear the \cTreeFae{} has some magic that might be worth stealing a tear of magic. You heard the troll muttering about it, that all Fae have one magical tear in their possession that can if drunk give you Fae magic. Not sure what that means, but sounds interesting and more power never hurt.

The guns, the cause of this whole meeting seem interesting; with your massive smartness figuring out how to build one should be easy. \cCleric{} seems to have one, the why hardly matter when you could take it from him. 

For someone with so many plans in term of war you do not have much of a plan. Peace could be interesting let the other die for your people. But you really don't feel that strongly and if you could get a few magical nick-knacks then you might just feel confident enough to crush the stupid humans. You could go either way. Though being supreme leader would be pretty great, it makes sense because you are the smartest.

You are the little guy with big plans.

\begin{itemz}[Goals]
  \item Obtain the \iOrbofPower{}
  \item bptain the \iTearofMagic{}
  \item Build a golem
	\item Steal any guns you can find to shoot people with
	\item Make everyone repsect you however you can
\end{itemz}

\begin{itemz}[Notes]
  \item You start wanting peace with the humans, but can change your mind easily 
  \item You know \cOnyx{} can help with the golems
	\item The Troll my know more about stealing Fae magic
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cTroll{}} An idiot who thinks they are a poet
  \contact{\cOnyx{}} An idiot who is old, powerful, and much less wise than \cOnyx{\they} think
	\contact{\cVampire{}} An idiot who is the head of the Lore Masters and full of \cVampire{\themself} for some reason
	\contact{\cCleric{}} An idiot who seems to have a gun
\end{contacts}

\end{document}
