\documentclass[char]{guildcamp2}
\begin{document}

\name{\cLich{}}

\cenquote{``Fusing intelligence with the power of undeath requires inspiration of the darkest kind.''}{-- Havengul Lich}

It has been 587 years that you have been wandering this plane, perfecting your craft. You were born a wealthy child in Tordin; from your first word, ``dead,'' you have seemed most in tune with the thin line separating heartbeats from silence. You often make a point to remember your past--you would lose all semblance of humanity if you didn't. Understanding the human mentality is the key to anticipating them. In your state of undead perfection, memories remain as crystal clear as the Phylactery which contains your soul, never fading. The same goes for your grudges. To this day, the thought of your bitter enemy, that pompous, patronizing, pest \cVampire{\full}, still sets your teeth on edge. The two of you have never gotten along. Your rivalry was born as you two were; your families hated each other with a passion and the two of you have maintained tradition. While you pursue knowledge and mastery of arcane powers in order to grow more powerful and control ever stronger minions, \cVampire{\formal} seems to accumulate and hoard knowledge for its own sake, all the while being insufferably arrogant about it. And the despicable hypocrite looks down on your zombies, as though \cVampire{\they} doesn’t command undead too! 

You and \cVampire{\formal} have been at war for centuries, but the oncoming conflict with humans offers a convenient opportunity if you are able to ensure that \cVampire{\their} troops are deployed in the coming battle, and you can avoid committing your own. In the chaos of war, you shall be able to finally take over the land controlled by \cVampire{\them} while \cVampire{\they} is off fighting. However, you must also ensure that \cVampire{\formal} is not elected Supreme Commander of the monster army -- even if you manage to seize \cVampire{\their} territory, the revenge \cVampire{\they} would be able to exact against you as Supreme Commander is\ldots{} troubling.  The only thing more troubling would be if \cVampire{\they} manages to pull off a certain, powerful ritual you know \cVampire{\they} has been working on.  You don’t know the exact details, but it has something to do with enhancing the innate vampiric domination (mind control) ability.

Yet as much as you hate \cVampire{\full}, what you are more sure of than anything is that you cannot let the humans get any stronger. You are pleased that \cOnyx{} has called the council to discuss this because no army can fight off the humans alone.  Living humans seem to be able to overpower your minions in a toe-to-toe fight, even poorly armed. To your great displeasure, you witnessed a hired mercenary destroy three of your strongest minions using that blasted new contraption they have.  You fear that an army of humans outfitted with such weapons would be nigh unstoppable.  You won your last pitched battled with the humans only by allying with the dragon \cRed{} and using scorched earth tactics; when the human invaders entered the large forest separating your territory and \cRed{}’s, the two of you set it ablaze, decimating their army.  The fact that the entire forest was destroyed in the process was beyond irrelevant--who cares about trees, anyway?  Ents, apparently.  The leader of their faction, Strong Branch, has had it in for you and \cRed{} ever since.

\cRed{} is the founder and leader of the Power Society, which you gladly joined shortly after it was founded.  It suits your ends of maximizing your own sorcerous might alongside like-minded monsters.  While you detest most living beings, being a lich can be a lonesome existence, and even you desire the company of your equals on occasion.  Too bad there are so few of those.  To this end, you have decided that it is time you took on an apprentice, some promising human sorcerer interested in embracing the power and immortality of undeath to become a lich alongside you.  Their power will never match your own, of course, but it would be useful, and less lonely, to have a proper assistant.  You have prepared a tome of your accumulated knowledge of undeath--the \iAncientSorcery{} --which, in the right hands, will allow its user to undergo the desired transformation upon their death.  You're not sure how to find a human wizard willing or coercible enough to undergo this process, other than capturing one in the coming battle, but the demon \cDemon{\full} may have some idea. \cDemon{\they} is in the business of trading information and corrupting souls, after all.

What your withered heart yearns for far more than companionship, however, is the power of raising beasts and monsters to do your bidding as well as human corpses.  You've played with this fantasy for a while now but haven't made much progress.  When you noticed the humans in the village nearest to your secluded home in a musty castle had begun making more and more of those loud destruction machines, you realized you needed to redouble your efforts.  Thus far, you have made great strides in improving your plans for what you know will be the height of your career. You are now thoroughly versed in raising weak monsters, e.g. imps, dire rats, etc., and know how to go about gaining the knowledge to raise more powerful monsters.  You would welcome the opportunity to raise a monster of legendary power, like Onyx himself, to serve you, but in order to do that, \cOnyx{\they} would have to be dead. And to slay \cOnyx{\them} you would undoubtedly need a massively powerful artifact, like the \iSwordofIce{}.  Conveniently, you believe the sword to be somewhere in Onyx’s castle.

You learned one interesting piece of information recently while interrogating the zombie you raised from a human cleric you had killed.  Your new minion told you of the god he had served, Groznak, God of War.  Before your other minions finally managed to slay him, this cleric, in life, bore a powerful aura you found both painful and unmistakable.  Humans worship many gods, most of them foolish fabrications, but what you sensed here was true power.  Much to your dismay, you sense the power of Groznak emanating from something, or someone, here at this war council.  You cannot pinpoint it, and you do not know what it could portend, but it is one more complication in an already precarious situation.

As a lich, your soul is stored within a magical gem, your Phylactery, which resurrects you if your body is destroyed, so long as the gem is intact.  You normally hide it in a carefully secured location, though you cannot go far from from it or you begin to weaken.  Knowing that this war council could take awhile, you brought the Phylactery with you and hid it in the deepest recesses of Onyx’s cavern, behind many layers of traps and monsters.  You have the ability to sense when someone is approaching your Phylactery, and you can teleport to it at any time, though that may not always be advisable--if both the Phylactery and your body are destroyed, your undeath will come to an end and you will pass beyond the veil of final death, never to return.  The very thought of it sends shivers through your already cold, lifeless body.

\begin{itemz}[Goals]
  \item Protect your Phylactery at all costs. AT. ALL. COSTS. 
  \item Learn how to raise powerful monsters. If possible, orchestrate to raise \cOnyx{}.
  \item Defeat the human army, but without risking the complete annihilation of their species. Corpses are beautiful and you need to rule them, but if all the humans die, you will lose your supply.
  \item Prevent \cVampire{\full} from being elected Supreme Commander, or from completing \cVampire{\their} mind control ritual.
  \item Find a way to acquire a human sorcerer to corrupt with the \iAncientSorcery{} so that you can have a lich apprentice.
\end{itemz}

\begin{itemz}[Notes]
\item You have no soul. Your phylactery holds what is left of your soul after a number of terrifying and brutal rituals that you underwent to become a lich in the first place. You may not interact with mechanics that require you to have a soul.
\end{itemz}

\begin{contacts}
  \contact{\cOnyx{}} The elder dragon leading the council.
  \contact{\cDemon{}} A powerful demon known for dealing in information.
  \contact{\cVampire{}} A rival ruler of the undead faction. \cVampire{\Their} ideas are vastly inferior. Perhaps \cVampire{\formal}'s only respectable quality is that \cVampire{\they} is the (overly) proud leader of the \bLoremasters{}.
  \contact{\cEnt{}} One of the oldest monsters in the land. \cEnt{\full} has let \cEnt{\their} distaste for you be well-known.
  \contact{\cRed{}} A powerful red dragon whose territory adjoins yours, and leader of the Power Society, of which you are a proud member.
\end{contacts}

\end{document}

















%\documentclass[char]{guildcamp2}
%\begin{document}
%
%\name{\cLich{}}
%
%\cenquote{``Fusing intelligence with the power of undeath requires inspiration of the darkest kind.''}{-- Havengul Lich}
%
%
%It has been about 587 years that you have been wandering this plane, perfecting your craft. You were born a wealthy child in Tordin; from your first word, ``dead'' you have seemed most in tune with the thin line separating heartbeats from silence. You often make a point to remember your past, you would lose all semblance of humanity if you didn't. Understanding the human mentality is the key to anticipating them. When you reminisce, you never allow yourself to think too much about your rival, that over-pompous, detestable \cVampire{\full}. The two of you have never gotten along. Your rivalry was born as you two were; your families hated each other with a passion and the two of you maintained tradition. You and \cVampire{\full} have been at war for centuries; if you are able to ensure that \cVampire{\their} troops are deployed, you can then avoid committing your own. In the chaos of war, you shall be able to finally take over the land controlled by \cVampire{\them} while \cVampire{\they} is off fighting. What you are more sure of than anything is that you cannot let the humans get any stronger. You are pleased that \cOnyx{} has called the council to discuss this because no army can fight off the humans alone.
%
%Unfortunately, your strategy of remembering hasn't been working out too well. The living humans seem to be able to overpower your minions in a one-to-one battle unarmed. To your great displeasure, you witnessed a hired mercenary destroy three of your strongest minions using that blasted new contraption they have.
%
%What your nonexistent heart yearns for is the power of raising beasts to do your bidding as well as human corpses. You've played with this fantasy for a while now but haven't made any progress. When you noticed the humans in the village near your secluded home in a musty castle had begun making more and more of those loud destruction machines, you realized you needed to work. Thus far, you have made strong strides in improving your plans for what you know will be the height of your career. You poured over every book you could find, but all your research led to a plateau when several texts referenced a single book with the secret of capturing monster souls. When you attempted to piece together the missing information, you were somewhat successful in that you now are thoroughly versed in raising weak monsters, e.g. goblins, dire rats, etc.  
%
%
%\begin{itemz}[Goals]
%  \item Learn how to raise powerful monsters.
%  \item Raise \cOnyx{}.
%  \item Protect Phylactery.
%  \item You want to kill the humans. Corpses are beautiful and you need to rule them.
%  \item Acquire the legendary \iSwordofIce{} to slay \cOnyx{}.
%\end{itemz}
%
%\begin{contacts}
%  \contact{\cOnyx{}} The elder dragon leading the council.
%  \contact{\cDemon{}} A powerful demon known for dealing in information.
%  \contact{\cVampire{}} A rival ruler of the undead faction. \cVampire{\Their} ideas are vastly inferior. Perhaps \cVampire{\full}'s only useful quality is that \cVampire{\they} is the proud leader of the \bLoremasters{}.
%	\contact{\cEnt{}} One of the oldest monsters in the land. \cEnt{\full} has let \cEnt{\their} distaste for you be well-known.
%\end{contacts}
%
%\end{document}
