\documentclass[char]{guildcamp2}
\begin{document}

\name{\cMinotaur{}}




\cenquote{``Not every intelligent being is interested in treasue and lost knowledge...or even the basics of speech.''}{-- Ruinous Minotaur}


You start munching on the goat leg before you, pieces of meat fall from your maw as you attack the bone with your sharp teeth. Chewing bone helps strengthen your bite and lost meat can fall for the gremlins. One of them comes to you with a scroll. You bang your fist on the crude table out of annoyance; you take a massive swig from your goblet and gulp as saliva and lost wine dribbles down the front of your hairy chest. 

``What this?'' you grunt loudly in the face of the gremlin. It whimpers, drops the scroll, then runs off, giggling. Picking up the scroll, you begin to read.

\emph{Greetings mighty war leader,}

    \emph{I write to you now out of desperation that I know we all feel, our days are numbered. The humans press further into the lands we call home.}

It seems that the old black dragon, Onyx, has decided to call together a council to discuss the human problem. You toss the scroll aside and return to devouring the rest of the three goat carcasses before you.  

``Hmm,'' you think, ``I wonder who will be at the meeting. Surely that old windbag would've invited the leading representatives of other factions, likely at least one undead, one fae, maybe a few others.'' Likely the fae will want to make peace with the humans, but maybe you can garner favor with the undead to help you enslave the humans. You need more intelligent minions to test your mazes; these gremlins are nearly always a waste of your time. You mentioned your desire for human playthings to your friend, \cBasilisk{}, who also expressed interest in human cattle. When you sent a note of inquiry to \cDemon{} (someone who you don't like talking to because of \cDemon{\their} smug attitude but always go to for the immense knowledge and resources \cDemon{\they} possesses), the only response you got was one indicating that half of the ritual was located in a dungeon in the old black dragon's castle. If you can get enough support, maybe you can go through the dungeon and attain half of the recipe. Where would the other half be?

``I wonder if the Sphinx will be there,'' a grimace grows on your already frowning face, ``Surely Onyx wouldn't have skipped over such a powerful weapon as the Sphinx. The Sphinx may be annoying and verbose, but at least you know that \cSphinx{\they} has the power to turn the tide in a war. This time I'll show that wordy windbag who is the better puzzlemaster!''
You have never felt that you could trust that annoyingly cryptic beast and your rivalry is legendary amongst those who follow puzzles. You don't understand the point of talking so much. In fact, your own language skills are so underdeveloped that you only speak in single syllable, though your thoughts are profound. You will finally show \cSphinx{} who is the true master of puzzles by completing your masterpiece! You are close to figuring it out, you just need some fresh perspective. Maybe someone at the meeting will help give you inspiration. If \cOnyx{} wants to discuss a solution to the human problem, there will likely be discussion of war and slaying the humans; \cSphinx{} will surely remain neutral for whatever silly reason until there is a vote of some sort. You know you can't risk an invasion by the Sphinxâ the mind-bending attacks of the Sphinx would surely wipe out all but your mentally-tough minions, and none of those will be physically capable of bringing \cSphinx{\them} down. It would be better to wait and see what \cSphinx{} commits to before making a public commitment of your own. After all, making a public commitment is separate from what you physically commit to doingâ words are not as powerful as the body. Maybe you and your supporters can band together and enslave the humans despite the inevitable vote at the end of this meeting.

You are a proud, Warrior member of the Power Society. The Society encourages its members to become as strong as possible. There is no discrimination as long as you can hold your own in a one on one battle. For obvious reasons, no weaklings are allowed to join; those members who work to gain presence in politics are still chosen by their physical prowess as well as mental.  You and the strongest of your ancesters have always been members; your family has served the Society so well that you didn't even need to pass a trial to prove yourself! The values of the Society are manifold, but you appreciate that the direction the Society has taken over the last fifty years has moved towards a more secret influence than in the past. You find the politics, while absolutely not your mug of ale, necessary for lasting power. The Loremasters Guild doesn't seem as if they have any real presence in Astyria because they mostly just shut themselves in the great Astyrian Library and ignore the world. You imagine every Loremasters member must never see the sun because they are always sitting bent over tomes. The Power Society doesn't mean as much to you as it did to your father, but you still participate fully in whatever tasks \cRed{} asks of you. You are a reliable member, though you are not an officer; you never really wanted to be an officer, you would prefer to spend that time in your mazes, perfecting them. 


\begin{itemz}[Goals]
  \item Enslave all humans!
  \item Finally design your maze masterpiece!
  \item Put \cSphinx{} in \cSphinx{\their} place by forcing \cSphinx{\them} into your masterpiece maze.
  \item Aid in the \bPower{}'s goals. 
  
\end{itemz}

\begin{contacts}
  \contact{\cOnyx{}} The elder dragon leading the council.
  \contact{\cDemon{}} A powerful demon known for dealing in information.
  \contact{\cBasilisk{}} A friend. You two enjoy forcing humans to ``play'' with you.
\end{contacts}

\end{document}
