\documentclass[char]{guildcamp2}
\begin{document}

\name{\cOnyx{}}

\cenquote{We must all hang together, or assuredly we shall all hang separately. -Ben Franklin}

	The world as you know it has ended. You are an ancient, black dragon, wise even beyond your formidable years. You recognized that the world was about to change when the smell of black powder first reached your nostrils. Once, monsters ruled the land, and the humans were nothing but a pesky thorn in your side as you battled for dominance among the great leaders of the other monsters. At that time, the world was in a deadlock between monster races, with humans doing all they could to not be overwhelmed by monsters, and all you had to worry about were a few pesky adventurers who might get the drop on you. Now entire human armies march, laying waste to monster kingdoms. Already they have killed your good friend, the king of the Manticores, and driven his people to extinction. They have steadily pushed back the forces of the monsters, slowly, but surely, heralding the extinction of all monster kinds. 
	
Monsters were never meant to unite into a single force. Occasionally, short lived alliances are formed to deal with an immediate threat, but it always falls to pieces once the ``discussion'' of how to divide up the spoils begins. Until now, it hasn't really mattered. Humanity were little more than pests. But now, it is the humans who pose the greatest threat to monsters. 
	
It seems that it is in every monster's fundamental nature to resist unity. And yet, you have set yourself against this seeming impossibility, because the only other option is your own destruction, and that of all monsters, and you will not stand for that. This is why you have called this council. You have the wisdom of age to see that the only way to drive back the humans is to unite. You and the other monster leaders must stop all the infighting amongst the monster species and mobilize your armies to combat the human horde which is descending upon your lands.  
	
In addition to getting an alliance formed, you  know that an army must have one supreme leader, not just many different equal leaders, or it will inevitably be defeated. Therefore, there will be a vote for the supreme leader of the monster force. You have no particular candidate in mind yet, but they must be wise, level headed, and have their number one goal as the preservation of monsters. If no one else steps forward, you are willing to nominate yourself.
	
To complicate matters, you know that some monsters have been approached by human diplomats with offers of peace. You have not received one, as you try to make it a policy to eat every human you see on sight, and you deeply distrust humans and their motivations. However, part of wisdom is accepting new possibilities. If the human's offer of peace is genuine, you would be willing to accept it. But the burden of proof is on any human foolish enough to wander within range of your powerful claws. One way or another, you will see to the preservation of all the races of monsters; this council is intended to do just that.

You are not surprised that every monster leader you have reached out came to this council, despite it's unorthodox intent. This is in no small part because you are known to be respectful of your equals among the other monster leaders, and will tolerate no murders at this council. Violence is inevitable among the delegates, but you will not have a monster leader killed on your watch. Towards that end, you have hidden an extremely powerful Orb of Resurrection deep in the dungeons. This should, hopefully, keep your guests alive for long enough to get the job done. But if someone becomes so unruly they have to be killed, you suppose you will have to destroy the orb. It may also have only so many charges (you don't know exactly how many,) so you will have to be cautious.

The other part of protecting the delegates is maintaining the wards. There are 3 wards scattered across your castle that keep wizards and other unwelcome magical beings out. These are the same wards that have allowed the monster leaders to teleport in. Their care and maintenance is of utmost importance to maintain security at the council.

Still, there are risks in calling monsters to your castle. As one of the oldest dragons on the continent, you have a massive treasure room with many priceless artifacts; and everyone knows it. You expect that some delegate or another will try to steal them from you. You are highly possessive of your treasures and will only let someone into your treasure room for a \emph{very} good reason, and even then, only with you in attendance.
	
As something of a side note, many years ago you had a son. You named \cRed{\them} \cRed{}, and then abandoned \cRed{\them}. It might seem harsh, but it is the reality of this world that many cruel things happen. You wished to teach your \cRed{\offspring} to stand on his own. From what you hear, \cRed{\they} is now the leader of the Power Society. Seems your strategy worked.

Seeing your son again has had the inconvenient effect of bringing to the surface an emotion that you had thought yourself incapable of feeling. In your age, you have become lonely. There is no monster species that could fulfill your desire for good company, but you have heard rumors of magical constructs, and one of them could provide you with the company you desire. Still, you will probably have your claws full with the council, so you may not get around to researching this yourself, but you aren't above liberating a construct from someone else.
	
	
	
	\begin{itemz}[Goals]
  \item Make sure the council reaches a decision that will preserve monster kind.
	\item Keep the peace between the delegates; if a delegate dies before sending  his army, that army will not be sent.
	\item Keep people out of your treasure room.
	\item Maintain your wards.
		\item Find a way to acquire a golem for company.
\end{itemz}

\begin{contacts}
  \contact{\cLich{}} That Lich is looking at you strangely, almost covetously. You'd better keep an eye on him.
	\contact{\cRed{}} Your \cRed{\offspring}. \cRed{\They} has made quite a name for himself, but despite what he might think, is \emph{not} in a position to take over your position as the strongest and wisest dragon on the continent.
\end{contacts}

\end{document}

