\documentclass[char]{guildcamp2}
\begin{document}

\name{\cRed{}}

		\cenquote{Well, I grew up quick and I grew up mean//My fist got hard and my wits got keen. - Johnny Cash}
		
Finally! They've finally recognized your greatness. Ever since your \cOnyx{\parent} left, you've had to fight  for respect. It is a common misnomer that Dragons are bad parents or that they leave their offspring to fend for themselves. Only those beyond saving are abandoned by their parents, and even then, usually not until they've given it a good try for a few centuries. \cOnyx{} abandoned you and your mother a mere three decades after you were hatched. Everyone knows that \cOnyx{} left you, and assume it was for good reason. It made every day of your youth a living hell.  
		
Every time you introduced yourself to someone new, they would laugh at you for being \cOnyx{}'s failed brat. So you would bash in their head. The constant fighting made you the roughest, toughest dragon in the entire southern Dragon kingdom. You fought your way through the ranks of the army and became the youngest war leader that the southern Dragon kingdom's ever seen. No one alive disputes the fact that the only dragon more fierce than you is giant black dragon, your \cOnyx{\parent}, \cOnyx{}. You hate your \cOnyx{\parent}, and you've sworn an oath to kill \cOnyx{\them} and take \cOnyx{\their} place as the undisputed master of all of the dragons on the continent of Astyria.

Now you are faced with a golden opportunity. \cOnyx{} has \emph{finally} recognized how great you are by inviting you to this council and asking you for your army. How far the great have fallen. He must be weak, if he's asking for help against the pathetic humans. This is the perfect time to fulfill your oath.

No human has ever set foot in the southern kingdom, thanks to your stalwart army and your tactical brilliance. There was one close call however, that you suppose is worth mentioning. Not so long ago, an army of humans managed to penetrate the monster lands right to your very border. Only through a temporary alliance with \cLich{\full} did you manage to rid yourself of those pests. Still, after the scorched earth tactics you used, you don't expect they will be foolish enough to try again. You and your army burned the entire forest in which the humans had taken refuge. You congratulate yourself regularly on such a brilliant tactic, but \cEnt{\full}, the leader of the Ents, sees things differently for some stupid reason. \cEnt{\They} has had it out for you ever since.

You are undoubtedly the most clever dragon in Astyria, but you find yourself needing to prove it to everyone yet again. If you send your force to deal with the human ``threat'', you demand to be the supreme commander, as you're far and away the best choice.  With you in command, it will be a trivial matter to squash the pathetic humans.
		
As part of your rise to power in the southern dragon kingdom, you became the leader of the Power Society a few centuries back. The society could use more members, and the leaders of the other monster factions seem a reasonable place to recruit subordinates. One of the things you hope to accomplish through the society tonight is raiding \cOnyx{}'s treasure room and relieving \cOnyx{\them} of some powerful artifacts. After all, it's about time you started your own horde of treasure and \cOnyx{} has the best stuff. You've heard rumors that he has a sword that has the power to slay dragons, an Orb of Power, and even a few fragments of a second mighty sword. If you could find all of the parts to the sword, you could reforge it into a mighty weapon.		

	\begin{itemz}[Goals]
	\item Become Supreme Leader of the alliance against humans. Make sure you are commanding as large a collection of armies as possible.
	\item Recruit as many people as possible to the power society.
	\item Kill \cOnyx{} to extract your revenge. If that proves temporarily beyond your means, embarrass \cOnyx{} as much as possible by causing problems.
	\item Collect all the \iVorpalSwordofWonder{}s and find a way to reforge them into a mighty weapon.
\end{itemz}

\begin{contacts}
  \contact{\cOnyx{}} The black dragon who called the council. Most people believe that \cOnyx{\they}'s the strongest dragon Astyria has ever known. You intend to prove that you're better than \cOnyx{\them}.
	\contact{\cMinotaur{}} A member of the power society.
\end{contacts}

\end{document}

