\documentclass[char]{guildcamp2}
\begin{document}

\name{\cSphinx{}}

\cenquote{``A riddle is nothing more than a trap for small minds, baited with the promise of understanding.''}{-- The Author}

As the creature known exclusively for mental prowess, you stand tall before your peers. You don't like interacting with the physical world about you, and that works for them because no one seems to enjoy listening to your beautiful riddles. Your entire being has been centered around your glorious word puzzles and you find nothing wrong with that. Everyone seeks you out for your amazing lingual acrobatics of the tongue! Your riddles are auditory art and you spend hours on perfecting them. If someone were to ask you what your greatest challenge would be, you would undoubtably admit that you find it exceedingly difficult to keep your riddles challenging but mundane enough for the less-devoloped brains around you. You affectionately tolerate all other life forms, but being as unique a creature as you are, you know that not everyone can understand your existence. You are the only one of your kind, and you are fine with that---well, you wouldn't mind having company, or having someone HAPPY  to see you once in a while, but you know that speaking in a non-cryptic manner is impossible! You have already evolved to speak in such a manner that you aren't speaking in full riddles every statement you make, but speaking in straight, plain, boring wording is absolutely beyond you. One word sentences are a faraway concept! You have no idea how creatures around you manage it!

Something that is able to bring your head out of your own world is your deep rivalry with \cMinotaur{}. Oh how you and \cMinotaur{\they} fight over who is the greater puzzle master! You know that manipulating words to play with the mind is something that only geniuses are capable of and you are the greatest manipulator of words Astyria has ever seen! You received notice of the \cOnyx{}'s meeting before \cOnyx{} even wrote you an invitation; you felt the message sweep into your consciousness while your brain was seeking inspiration in one of your famous trances. That minotaur has always insisted that physical puzzles, like mazes, are superior to mental puzzles, like riddles, because mazes can trap anyone whereas riddles only trap some. You disagree! Your riddles are magnificent works of art! The nature of the riddle is to test the subject and mental prowess is to be rewarded! The fact that anyone can be tricked by a maze is something that you despise; after all, that would mean that mazes treat the mentally strong the same as the physically strong! You completely reject the aforementioned concept. 

With all of your personal philosophies in mind, however, you feel that it would be nice to not be shunned. Your tongue is strong, like your mind, but that doesn't mean that you loathe the other creatures of Astyria. You like humans because they find great interest in your riddles; they don't seem to mind that you speak cryptically---in fact, they seem to want to worship you! As far as the question of how to react to the human ``gun'' invention, you remain firmly neutral. No humans have decided to attack you, but you are aware that they will in one of the many possible futures. In order to determine which side of the argument you choose, you have decided to give your vote to the better of the two sides, in terms of riddle-solving. The humans you have spoken to have mostly been disappointing, but you have determined that they are currently winning the competition in your mind. You have decided to ask a riddle of each creature at this meeting and if ten or more of them are able to answer your riddles correctly, then you will take their side. Your vote is extremely important because you have a series of mental attacks that cripple your foes. Your signature mental attack has been known to turn the tide of wars past. As you are readying yourself to be teleported, you make a snap decision that you will find some way to translate your cryptic manner of speech to a means that is capable of being understood by the average creature. 


\begin{itemz}[Goals]
  \item Find a way to communicate with your peers.
  \item Determine which side of the humans versus monsters war you are on through riddles.
  \item Show \cMinotaur{} who is the REAL puzzle master!
  \item Figure out a way to make everyone your friend.
 
\end{itemz}

\begin{contacts}
  \contact{\cOnyx{}} The elder dragon leading the council.
  \contact{\cDemon{}} A powerful demon known for dealing in information.
  \contact{\cMinotaur{}} Your rival in the puzzle world. Your mental puzzles are far superior. 
\end{contacts}

\end{document}
