\documentclass[char]{guildcamp2}
\begin{document}

\name{\cTreeFae{}}


Last night was one of the most remarkable nights of your life.  In all your centuries of existence, you've been capricious and frivolous, never seeking a higher calling than bedecking early morning blossoms with dew or painting the autumn leaves in fiery shades of red and gold.  (For as long as your attention span lasts, of course.  The fae folk of your Summer Court complete tasks you forget to finish.)  But last night you and your counterpart in the Winter Court, \cBabyFae{\intro}, were summoned to see the Oracle.

Actually, you were in the middle of dancing in some wheat fields, which you were loathe to leave, but the Oracle cannot be denied.  At this meeting, she spoke in ringing tones of the alignment of stars and prophesied the rising of Ezekiel, the King who will unite all fae folk, old and young, Summer and Winter alike.  She impressed upon you and \cBabyFae{} the importance of cooperation in performing the ritual to raise him.  (The two of you haven't always gotten along, but it looks like you'll have to.)  It must be done using a gem from the Tomb of Ezekiel, whose location was lost long long ago.  However, she has sensed that one of the jewels is not far from here.  In fact, it will be at the council meeting the ancient dragon \cOnyx{\intro} is holding to coordinate action against humans.  You were planning to attend anyway, but now you have all the more reason to go.  The Oracle then gave you the Tome of Ezekiel, which describes the elaborate ritual you must perform.  You and \cBabyFae{} swore to her that you would not fail.

Easier said than done, of course.  There are just so \emph{many} interesting things you want to do.  Your friend, the ent \cEnt{\intro} who lives in the same forest as you, has long harbored the hope of turning all humans into trees.  Pointing out that humans wouldn't be so quick to cut down trees if they \emph{were} trees, \cEnt{\they} convinced you that the only way to save your home is to perform a ritual to turn all the humans into trees.  You have only been at this council meeting for a few minutes, but the two of you have already persuaded the troll, \cTroll{\intro}, to join you.  \cTroll{\They} has no great love for humans either, since they have an irritating habit of mistaking sleeping trolls' mouths as caves and trying to light fires in them, and then trying to kill the trolls that wake up and fight back.  Hopefully, with all three of you, you can succeed in pulling off the ritual.  (With so many spells that must be performed, you've brought some magical fruits with you, in case they come in handy.)

And then there is the vote on how to fight the approaching human horde.  The others keep badgering you over whether you plan to deploy the Summer Court's army, but you are hesitant to commit yourself.  You think that turning humans into trees is a much simpler, cleaner alternative.  You'll have to discuss deployment with \cBabyFae{} and see if \cBabyFae{\they} thinks it's a good idea.

There are other distractions as well.  Shortly after you arrived, you saw a very striking djinni, \cWizard{}, walking around.  Mmm, eye candy.  You introduced yourself, naturally, but you'd like to pursue the acquaintance.  Also, while listening to the dragons rant about the so-called human ``heroes" who persist in hunting them down, you suddenly realized just how fun it would be to become an adventurer.  No responsibilities, no long-term plans -- you could do anything you wanted, anytime you wanted.  What freedom!  You're in luck -- your fae nose tells you that a human is present.  Perhaps if you have time, you can figure out who it is and ask about adventuring (before you turn it into a tree).  

While you're pursuing all these goals, you also have to worry about others trying to steal your magic.  Fae magic is renowned for power (it can cure ugliness, for one thing), and you wouldn't be surprised if someone here wants it.

One thing is certain -- you won't have to worry about getting bored at this council meeting!


 
\begin{itemz}[Goals]
  \item Raise Ezekiel so he can unite all fae folk.
  \item Help \cEnt{\intro} and \cTroll{\intro} turn all the humans into trees.
  \item Make sure no one steals your fae magic.
  \item Become an adventurer -- it sounds really fun!
\end{itemz}


\begin{contacts}
  \contact{\cOnyx{}} An ancient dragon who called this council meeting.
  \contact{\cBabyFae{}} Your counterpart from the Winter Court, with whom you have an uneasy alliance.
  \contact{\cEnt{}} An ent who lives in the same forest as you, who wants to turn humans into trees.
  \contact{\cTroll{}} A troll you just met at this council, who also wants to turn humans into trees.
  \contact{\cWizard{}} A djinni you just met at this council, to whom you are attracted.
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.

%\starttag{abils}
%  \ability{Amazing Powers}{You can do strange and amazing things.}{I
%  do something strange and amazing.}
%\endtag


\end{document}
