\documentclass[char]{guildcamp2}
\begin{document}

\name{\cTroll{}}


%% quote examples
\bigquote{``I'm coming to gobble you up''}{-- Three Billy Goats G
ruff}

A Poet and a troll. Two incongruous demons raging in the bowels of your essence. A monster whose wit is sharper than any gnashing teeth it may possess. They call you a fool and laugh, but their laughter is the cage of stenotype trapping them in the fruitless grip of damning expectation. They pity you for the determination you possess, but you in turn pity them for their tinted view of the world that lives in the dream of their visions, haunting their lives. The shades of past shape present. 

The cruelest of your critics is that snide, seditious, slandering sphinx \cSphinx{}, who believes that words are for building walls of riddles and confusion, not uplifting the soul on wings of glorious verse. You shall make \cSphinx{them} pay for \cSphinx{their} cruelty and cynicism this night, whether through tooth and claw or scathing verbal retribution.

The dove does not sing for the song alone, but sings to attract a mate and join in a duet, voices mingling in a harmony of profound noise. In that regard a magical quill is needed to capture and enthrall, enhancing the soft musing of your heart. A quill of magic to carry the magic of your words to the world--what more fitting magic could there be? In the hands of the dark prince of demonic danger \cDemon{} the quill lies--what task pure or vile will be needed to free this magical key to your poetic whimsy? 

Yet whimsy has taken over more than your dreams--it fills your heart to the brim, ever since you met her. \cTreeFae{}...\cTreeFae{\their} name itself is the melody of the winds, the song of the trees, and the music of the crackling fire. Like a sun rising over tranquil oceans stirred to fury by sudden storms, shattering all peaceful facades, your calm, vibrant heart was struck by the righteous fury of love that seeped throughout every pore of you large frame. An ally, unexpected but well met, has told you of a chance to win her:  A metamorphosis most extreme to twist the teeming human masses into trees, which you know \cTreeFae{} loves. This ally is already half tree himself, none other than the mighty ent \cEnt{}.

Dark clouds gather and peril rears its fearsome head, for the Djinni \cWizard{} has entrapped your love's shining heart in \cWizard{their} webs of treachery and lechery.  \cWizard{they} must die or be dealt with so that the waves may part and \cTreeFae{\they} may again see the surface of the beautiful sky of true love. If that bloody declaration does not convince \cTreeFae{} of the truth of your love then you shall have to seek a love potion somewhere. Just a splash on skin of your beloved and away will flutter any lingering doubt of your love. 

\cBabyFae{} the fae, the pale shadow of \cBabyFae{their} cousin \cTreeFae{}, may have the magic to change your shape and make you truly ideal in outward form to match the glorious luminosity of your soul. It would help you understand the true beauty of your soul and so the magic must be stolen or coaxed out of \cBabyFae{them} by whatever means necessary. You must claim the \iTearofMagic{} to gain this vibrant power of shifting shapes. 

Your army is strong and you really do not care what happens to your soldiers. They are all silly brutes who do not grasp the endless power of your nimble mind. You even have had to smash some of the foolish brutes from time to time. Perhaps you can use your army to garner fortune’s favor.  

Though the verse does not always come easily to you, there are times when inspiration floods you, mind, heart, and soul, with the blinding light of truth. At such times the words flow from your pen like pure waters from a spring. It is a pity that so few take you seriously, for you know that you have the bard’s tongue. When you received Onyx’s invitation to the war council, a new poem sprang unbidden to your lips with the force and intensity of a hurricane:

The three-headed serpent coils, cornered in its lair
Whilst all around it, the vengeful manlings prepare

Fangs flash bright, three heads quarrel over which shall strike
Heedless of the price to friend and foeman alike

One mouth holds venom, the second enslaves the will
The third brings change arboreal, woody and still 

Yet no matter which one strikes, the cost will be great
As it is with all choices made in fear and hate

But all is not lost, for a fourth path there may be
If, acting as one, all the heads can but agree

You have had precious little time to guess at its meaning, but if the “change arboreal” is the ritual which will turn humans into trees, then perhaps there are two other rituals--the other two heads of your figurative serpent--being considered by those gathered at the war council. You do not yet know what the “fourth path” could be, but if your poem holds true, then any of the three rituals will come with a heavy price. Thinking about such weighty practicalities when your mind should be filled with the music of poetry makes your head hurt. It is going to be one rough evening, but you have faith that love and poetry will guide you true, as they always have.

\begin{itemz}[Goals]
  \item Win the love of \cTreeFae{}, using \iLovePotion{} to do so if all else fails.
  \item Kill or utterly humiliate the Djinni \cWizard{}, who has stolen the heart of your love.
  \item Decide how to interpret your prophetic poem, and what to do about it. Complete the ritual to turn all humans into trees, for the sake of your beloved \cTreeFae{}, if you decide it is worth the price.
  \item Get and keep the \iQuill{} from the demon so you can compose a love poem to rival all that have come before.
  \item Obtain the \iTearofMagic{} from \cBabyFae{} in order to gain the ability to transform your body to match the radiant beauty of your soul...by any means necessary.
  \item Kill or utterly humiliate the sphinx for so cruelly mocking your poetry.
\end{itemz}

\begin{itemz}[Notes]
  \item You are neutral about your armies and their use
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cTreeFae{}} Your true love, peerless in beauty, wit, grace, and wisdom.
  \contact{\cEnt{}} Will help you complete the ritual to turn humans into trees.
  \contact{\cBabyFae{}} Though \cBabyFae{\their} beauty is but a pale shadow of \cBabyFae{\their} cousin’s, \cBabyFae{\they} possesses the power of transformation you seek.
  \contact{\cWizard{}} The vile scoundrel who has stolen your true love’s heart. 
   \contact{\cSphinx{}} The mocking, arrogant beast who has been your harshest critic.
\end{contacts}

\end{document}

