\documentclass[char]{guildcamp2}
\begin{document}
\name{\cVampire{}}

\bigquote{``Remember my friend, that knowledge is stronger than memory, and we should not trust the weaker''}{-- Bram Stoker, Dracula}

Many throughout the five hundred and eighty seven years of your unlife have come to hate you and fear the name \cVampire{\full}. Of course, the fools' petty emotions just make you laugh. They can scream and curse at you all they want -- you are too busy plotting and accumulating hidden lore care. If there is one thing you have learned in all of your long unlife, it is that knowledge is power. And you have a lot of knowledge, rivaled only by the likes of \cDemon{} and \cOnyx{}. Your lust for lore is why you founded the \bLoremasters{}. As its leader you can guide the other members on your quest to gain further knowledge. 

Your knowledge and stature have clearly impressed \cOnyx{}, as \cOnyx{\they} has entrusted you with being in charge of the dinner party this evening. It is the natural choice, as you will be by far the most elegant and eloquent being present. But convincing such a motley assortment of creatures to conduct themselves with any semblance of proper courtesy and protocol will be...challenging.  Still, you intend to do your utmost to make sure everyone is polite and that decorum is maintained.   

You were born in the human city of Tordin; growing up, life was perfectly acceptable other than the fact that everyone around you was a complete moron. Or at least, life would have been perfectly acceptable were it not for that bastard lich \cLich{}. You and that power-mad pile of putrescence go way back, back even before you rose from the grave. You vaguely recall that your families had some sort of long standing rivalry, but your loathing of \cLich{} goes far beyond some petty old feud. \cLich{\They} has no appreciation for poise, patience, or subtlety, as evidenced by the hideous, shambling minions \cLich{\they} so eagerly raises at every opportunity. You, on the other hand, long ago learned the value of maintaining a calm and dignified demeanor at all times, though that fool lich surely tries your patience. 

Still, you will have ample opportunity for spiting \cLich{} this evening.  For one thing, your spies have informed you that \cLich{\they} recently completed a manuscript containing all of \cLich{\their} arcane knowledge. ``It must be an awfully thin book,'' you jest to yourself, a slight smile passing across your pale lips. While it is unlikely that this ludicrous manuscript contains any useful lore, it would be worth getting your hands on it just to see the expression on \cLich{}’s bony face when \cLich{\they} finds out.

You also comfort yourself with the knowledge that \cLich{\they} will get \cLich{\their} comeuppance when you at last seize \cLich{\their} lands for your own and destroy the vile, stinking zombies that pass for \cLich{\their} minions. Your strategy is simple, but foolproof. The plan is to bide your time and let \cLich{} mobilize \cLich{\their} army, where most of \cLich{\their} disgusting zombies will perish fighting the human hordes. Meanwhile, you and your armies will stay back and seize \cLich{\their} territory, leaving \cLich{\them} a homeless beggar -- a most delectable punishment. 

Of course, if things look too grim and you are forced to mobilize your own armies against the humans to prevent your own extinction, you had best make sure to be chosen as Supreme Commander of the armies. You can think of no one better qualified than your illustrious self, and as Supreme Commander you can more easily ensure that \cLich{}’s troops are assigned to the front lines, there to be decimated; it is all zombies are good for anyway.   

You have never liked zombies; they give you and your brood of vampires a bad name. To be classified by ignorant fools and doddering scholars alike under the family of Undead with monstrosities such as they is not only revolting, it is insulting! They rot and drool and have no will or drive of their own, whereas you are the epitome of style and control. People call vampirism a curse, but it is a blessing, immortality and power. 

Yet all blessings come with a price. For your kind, the price is blood and darkness. There are precious few things you miss from your days as a human, but in your more sentimental moments, you often wish that you could again feel the kiss of sunlight upon your cold flesh without burning. Despite all your searching in dusty tomes, you have yet to find the piece of arcane knowledge that would grant you this wish, but you have heard that the Fae may possess such knowledge; and if they prove unhelpful or uninformed -- as most creatures do -- you could always try the \cDemon{}. For a price, \cDemon{\they} almost always has useful tidbits. 

As for the other price to your immortality, you know of no solution. Much as you hate to admit it, your fate is shackled to that of humanity, for it is their blood alone which sustains you. Therefore, the complete annihilation of the humans cannot be allowed. Enslaving them as livestock would be a beautiful solution. 

To that end, your research recently uncovered a powerful ritual which would boost your natural vampiric powers of psychic domination to a staggering degree. It unfortunately requires the cooperation of a few other beings of power, or you would have performed it already. This war council will be the perfect opportunity to enlist the necessary assistance, though you will have to be careful how and to whom you couch this proposal. If the other delegates knew just how much power the ritual will give you, that meddling lich might be able to turn them against you. If executed properly with the arcane knowledge you’ve gathered, you believe the ritual will not only allow you to enslave large swaths of humanity, but also control at least some monster species. 

After all, knowledge is power. *long, diabolical laugh*

\begin{itemz}[Goals]
  \item Find a way to walk in the sunlight safely.
  \item Complete the \gEnslaveRitual{}.
  \item Make sure everyone shows up at the dinner party on time and maintains proper courtesy and decorum.
  \item Frustrate the designs of the lich \cLich{}, and if possible obtain the \iAncientSorcery{} which he has written.
  \item Avoid committing your army if possible, but if you must do so, become the Supreme Commander of the armies, at which point it will be easy to maneuver the lich's armies into a bad position.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cLich{}} You really hate \cLich{\them} and have for a long time. He is a member of the Power Society.
  \contact{\cOnyx{}} A powerful elder dragon, well versed in lore, and host of this gathering. 
  \contact{\cDemon{}} A notorious information broker whom you both respect and, if you’re being completely honest, envy.
  Fae?
  Other Loremasters?
\end{contacts}


\end{document}











%\documentclass[char]{guildcamp2}
%\begin{document}
%
%\name{\cVampire{}}
%
%%% This sort of use of \updatemacro is covered in
%%% Extras/README-namemappings.
%
%%% quote examples
%\bigquote{``Remember my friend, that knowledge is stronger than memory, and we should not trust the weaker''}{-- Bram Stoker, Dracula}
%
%Many throughout the five hundred and eighty seven years of your life have come to hate you and fear the name \cVampire{\full}, of course the fools' petty emotions just make you laugh. They can scream and shout at you all they want -- you are too busy plotting and building knowledge to care. If there is one thing you have learned in all of your long life it is that knowledge is power and you have a lot of knowledge rivaled only by the likes of \cDemon{} and \cOnyx{}. 
%
%Your lust for knowledge is why you founded the \bLoremasters{}. As its leader you can guide the others members on your quest to gain further knowledge. Of course one piece of knowledge you seek and value above all others: knowledge of walking again in the sun. You have heard that the Fae may possess this knowledge, and it will be yours.   
%
%You were born in the human city of Tordin; growing up things where perfectly acceptable other than the fact that everyone around you was a complete moron, or they would have been if it was not for that bastard \cLich{}. You and that dried up shriveled old \cLich{} go way back, back even before you came back to life. You were both rich and you now realize arrogant with the entitlement of privileged youth. You have since learned to remain calm though that fool \cLich{} surely tries your patience, but \cLich{\they} will get \cLich{\their} comeuppance when you take the lands that should rightfully be yours. Your strategy is simple, but foolproof. The plan is wait and let \cLich{} mobilize \cLich{\their} army, losing most of \cLich{\their} disgusting zombies fighting the human hordes. Meanwhile, you and your armies will stay back and seize \cLich{\their} land, leaving \cLich{\them} a homeless beggar -- a most delectable punishment. Of course if things look too grim and you are forced to mobilize your armies to prevent extinction, then you had better be the supreme commander of the armies. You will only agree to mobilize if \cLich{} troops are on the front line too; it is all those zombies are good for anyway.   
%
%You have never liked zombies; they give you and your brood of vampires a bad name. To be bunched under the family of the undead with creatures such as them is completely revolting. They rot and drool where as you are the epitome of style and control. People call vampirism a curse, but it is a blessing, immortality and power. A blessing with one small cost, blood, you cannot let the blood dry up. As such the complete annihilation of the humans cannot be allowed. Enslavement of the human cattle is a beautiful solution. It would be an endless blood bank of waiting and willing slaves. You know of a ritual that has the power to enslave all humans on the continent, if such a thing were true it would be very interesting academically and practically. 
%
%One more thing, \cOnyx{} has entrusted you with being in charge of the dinner party. Make sure everyone shows up and is polite, decorum must be maintained.   
%
%
%%%%%%
%%% The itemz environment is a list environment similar to itemize.
%%% The typesetting is very tight, and matches that used by the lists
%%% at the end of character sheets.  It takes an optional argument that
%%% acts as a title for the list.  The enum environment is a similar
%%% variation of the enumerate environment, and the desc environment is
%%% similar to description.
%\begin{itemz}[Goals]
%  \item Find a way to walk in the sunlight safely.
%  \item Complete the \gEnslaveRitual{}.
%  \item Make sure everyone shows up at the dinner party on time and is polite.
%	\item Discourage rudeness among the delegates.
%	\item Avoid committing your army if possible, but if you must do so, become the supreme commander of the armies where it will be easy to maneuver the lich's armies into a bad position.
%\end{itemz}
%
%
%%%%%%
%%% List contacts, using \contact{<char macro>}
%\begin{contacts}
%  \contact{\cLich{}} You really hate \cLich{\them} and have for a long time
%\end{contacts}
%
%
%%%%%%
%%% \starttag{<tag>} <elements> \endtag 
%%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%%% whites, notebooks, cash, signs, ids.  These each correspond to a
%%% type of macro defined in Lists/.
%%%
%%% By using \starttag, you can give this character <elements> of the
%%% type corresponding to <tag>.
%%%
%%% Multiple uses of the same <tag> will simply add together.
%
%
%
%\end{document}
