\documentclass[char]{guildcamp2}
\begin{document}
\name{\cWizard{}}

Despite having an acute appreciation for all manner of arcane knowledge, you really have only the vaguest sense of how a djinni is supposed to act. Cryptic or straightforward? Forward-thinking or opportunistically shortsighted? Your ignorance of djinni behavior is turning out to be somewhat troublesome, seeing as you currently look just like one, and you happen to be surrounded by any number of creatures most of whom you are certain would rip you to pieces if they knew you were a human.

You are \cWizard{} Albelin, a prominent and rising member of Norbrook's Arcane Academy (not that any of the creatures here have even the slightest idea what that is). You seek out all magical knowledge and are not afraid to get your hands dirty to find it. One day while wandering the astral plane, you intercepted a mysterious and terse missive being carried by a baby air elemental. After easily hypnotizing and interrogating the elemental, you deduced that \cOnyx{}, an elder dragon, was attempting to unite a diverse array of races into a single army to oppose the human army currently on the march. \cOnyx{} had requested the aid of the djinni, who turned them down claiming that the djinni are busy with their own affairs trying to invade the ifrit and have no time for \cOnyx{\their} concerns. You aren't really as up-to-date on human politics as you should be, but you do know that with the recent development of gunpowder humans have proven themselves quite a competent adversary even against such powerful foes as vampires, demons, and dragons. It appears that \cOnyx{} is inviting the leaders of each race to a special war council. Realizing this opportunity isn't going to present itself again, you wipe the air elemental's mind, polymorph yourself into what you hope is a convincing-looking djinni, and proceed to the council.

You are not a military-minded individual. You suspect that, had you not ended up with the talent to become a powerful wizard, you might have been a passable ambassador or diplomat. If you had your way at this council, there wouldn't be any fighting at all. The monsters are hardly friendly and up until now have harassed and killed humans who stray from magically-protected cities with little fear of repercussions. But you also don't want things to escalate to an all-out war. Now that humans have firearms you suspect that the human army will come out on top unless \cOnyx{} manages to unite all the monster races together, but you know there will be huge losses on all sides. It's a long shot, but before \cOnyx{} manages to unite the armies together, you plan to find a group of monsters sympathetic to your cause and convince them to sue for peace with the humans. You have enough political influence that you could guarantee their safety as long as none of their troops take part in the battle. Even if few monsters are likely to be interested in peace, many of the more self-serving races such as goblins or fae might realize the benefits of saving their races from needless sacrifice. In any case, you are determined to try and delay or disrupt things to prevent as many of the war leaders as possible from committing their armies to \cOnyx{}'s cause.

You've only been at the conference a brief while, but you've already seen a frightening diversity of monsters. Most seem to be the leaders of their races and, despite your considerable skill as a wizard and experience as an adventurer, you're certain that many of them could crush you with little to no effort. Still, you are intrigued --- few wizards have ever had the opportunity to study living demons, liches, and dragons in close proximity. Some of these monsters are centuries old and you fully intend to take advantage of the chance to learn what you can from them.

There are four attendees that you've heard of before: the elder dragon \cOnyx{}, the demon \cDemon{\intro}, and the archlich \cLich{\intro}. \cOnyx{} has been around for longer than anyone can recall. Normally dragons \cOnyx{\their} age vanish into seclusion, so the fact that \cOnyx{\they} is taking such an active role in this conference is unsettling. \cDemon{} is far less widely known in human lore, but among wizards there are several records showing \cDemon{\them} to be an insidious information dealer. On one hand, you know that \cDemon{\they} has plenty of sorcerous knowledge you would pay dearly to have, but you know that you are not likely to come out ahead on any deals you might make. Still, you suspect \cDemon{} has or can point you to a copy of the long-lost \emph{Demonomicron}, a comprehensive history of demon-kind's many wars. Finally, centuries ago \cLich{} was one of the most powerful sorcerors on the continent. Obsessed with immortality, \cLich{\they} eventually achieved it but only by turning into a lich. You would pay dearly to find and examine \cLich{\their} phylactery; although most people who ask after a lich's phylactery find themselves rapidly disintegrating. \cLich{} has committed innumerable atrocities, so you would like to destroy the phylactery but you know they are notoriously hard to destroy.

You are an accomplished wizard, but your true expertise and passion lay in the history, design, and construction of golems. Imagine your surprise when you realize that this meeting is being held in the ruins of Zumwalt's laboratory, the greatest gnomish artificer ever known! Zumwalt also specialized in golems, and the chance to explore her laboratory is very exciting. You are certain that there are plenty of notes lying around that would be priceless to modern golemists such as yourself. If you find the right parts, you might even be able to build a golem of your own. Beyond its academic interest, such a golem could also help you avoid being crushed during your time at the council.

%Your polymorph spell is working just fine, but it doesn't last forever. Before three more hours elapse, you will need to find a polyp fruit and a quiet place to refresh your spell. Polyp is a wild fruit that grows in this area, so you hope you won't have to do too much searching.

You are a wizard, not a scientist or engineer. You vaguely understand how gunpowder works, but you leave the actual design and construction of guns to others more suited to the task. Still, before you got sucked into this war council you were mulling over plans to augment guns with magic. You still have the basic blueprints of your modifications with you, although you have no plans to work on them while you're here.

In your readings you know that monsters have their own analog of an ``academic community''. You don't know much about the specifics, but you are definitely interested and this is the perfect opportunity to find out more. You suspect that the more ``knowledge-oriented'' races like vampires, demons, and liches are likely the best ones to approach, but you will need to be cautious lest you get revealed as a human.

\begin{itemz}[Goals]
  \item Convince as many factions as possible that war is futile and that they should sue for peace with the humans.
  \item Prevent factions from committing their armies to the war effort by whatever means necessary.
  \item Acquire the Demonomicron; you hope that \cDemon{} can be convinced to help you with this.
  \item Find out more about (and possibly join) the monster's academic society.
  \item Find and examine \cLich{}'s phylactery.
  \item Acquire as many of Zumwalt's notes on golems as possible.
  \item Build a golem servant by scavenging parts from Zumwalt's golem laboratory.
\end{itemz}

\begin{contacts}
  \contact{\cOnyx{}} The elder dragon leading the council.
  \contact{\cDemon{}} A powerful demon known for dealing in information.
  \contact{\cLich{}} Once a powerful human sorcerer, now an even more powerful lich.
\end{contacts}

\end{document}
