\documentclass[blue]{guildcamp2}
\begin{document}
\name{\bAstyria{}}

You live on this beautiful continent known as Astyria. The land mass is immense and holds several rich biomes, such as swamps, mountains, plains, and an abundance of coast. Humans have long lived freely on this continent, mostly gathering around the coasts. Since the beginning of Astyria's existence, creatures with various racial variations have ruled their own areas of the continent; humans have been left to fend for themselves. Such has been the way since the beginning of the oldest memory; the known species have been: the proud minotaurs, the noble dragons, the manipulative demons, the gloomy liches, the pretentious vampires, the hardy Ogres, the flighty Djinni, the mischievous fae, the riddling Sphinx, the slow-moving ents, the slithering basilisks, the aggressive Trolls, and the crafty goblins. There was also a proud species known as manticores who were the first to go when the humans started to fight back. The humans have only just recently started to have an impact on monster survival with their recent technological leap---the gun!

Monsters have thrived on this continent of Astyria for as long as the two suns have been flying about the sky. Epic battles have been fought with rivers of blood staining the ground. No two species formed alliances, in the beginning. As time ticked on, monsters began seeing the similarities they held and started bonding based on those similarities. Factions of monsters have developed from those with similar interests. Two organizations have made their mark on the land as the two oldest factions; though their age is where their similarities end. One of the two societies are the Power Society, a hardy group of battletorn warriors who have fought their way to immense control over Astyria, both in politics and in brute force. The other society is the Loremasters Guild, a scholarly group of intellectuals who have found a niche as the single most reliable source of information as well as being a unit responsible for nearly all technological advances for the monster world. The Power Society is run by the up and coming visionary known as \cRed{}. The Loremasters Guild is run by the aristocratic and fastidious \cVampire{}.

{\bf A Brief Reminder of Astyria Lore}

Dragons -- Big, scary, flying lizards that breathe magical fire. The older they are, the more powerful and invincible they are. There is a legendary sword called the Sword of Ice that has been known to slay the strongest of dragons, but there is no historical documentation of its existence.

Ents -- These are tall, tree humanoids. They move slowly and is known for being passive. They regenerate when killed unless they are slain with magical fire.

Trolls -- These hulking humanoid creatures are often mistaken for rocks when they are sleeping. They too regenerate unless they are being slain with magical fire.

Liches -- These are undead mages. Liches are created when a necromancer decides to exploit his/her soul for power. A lich cannot be killed unless his/her phylactery, which holds the lich's soul, has been destroyed.

Vampires -- These are undead. Once human, a vampire is created from the bite of another vampire. Vampires are tricky as sometimes they can come back from death.

Goblins -- These small humanoids are looked down upon by their fellow monsters for their apparent weakness, but make up for any physical shortcomings with their brutal cunning. They don't often try to rise up the totem pole, but occasionally they do.

Fae -- Small , mercurial, mischievous, humanoid creatures who take delight in trickery. The fae are known for shapeshifting. They use their abilities to deflect attacks and manipulate humans into their traps.

The Sphinx -- The Sphinx is a creature beyond time. It is not indestructible, but the mental prowess and attacks of the Sphinx are legendary. 

Minotaurs -- Minotaurs, giant humanoid bulls with penchants for violence, are known for being zealous in battle. Their communication skills are shoddy at best. Their military strategy shows surprising intelligence.

Basilisks -- Basilisks, snakelike creatures, use their powerful ability to turn other creatures to stone.

Djinni - The djinni, who often grant wishes and have great magical power, are known to blink to safety when they are in danger of being killed. They can grant wishes only once a day.

Ogre -- These brutes are known for being dimwitted and smelly. Suggestible but stubborn, commonalities are unpredictable. Ogres have been everything from priests to cobblers, but never kings.

Demon -- Demons are spirits from the abyss who take great joy in collecting items of great value. They make deals whenever possible and can teleport. Few trust them, but some are charismatic. They always have information.

Souls -- Souls are a bargaining chip often used by demons. Monsters barter their souls the same way a farmer might barter their favorite livestock --- they may loan it in return for a considerable service, but generally with the intention of recovering it in the future (either by trade or by force.) Unless you know otherwise, losing your soul causes no specific loss of abilities or power.
\end{document}
