
\documentclass[blue]{guildcamp2}
\begin{document}

\name{\bLoremasters{}}

\cenquote{``Intelligence without ambition is a bird without wings.''}{-- Salvador Dali}

The Loremasters Guild is a scholarly group of intellectuals who have found a niche as the single most reliable source of information as well as being a unit responsible for nearly all technological advances for the monster world. It is in an often deadly rivalry with the Power Society.

You are a proud, faithful member of the Loremasters Guild. You spend hours poring over books, searching for the elusive secrets of the universe. The Guild encourages only the most dedicated scholars to join; members only increase rank when they are publicly witnessed as being martyrs for their research. Many view the members of the Loremasters Guild, as stuffy, dusty, weaklings but that could not be farther from the truth. In fact, the current leader of the Guild is the fastidious \cVampire{\full} who rules the Guild with an iron fist. Virtually no research is important or groundbreaking enough for the leader's approval. Though the current leader is strict and arrogant, \cVampire{\they} isn't there to be liked---something that \cVampire{\they} knows very well. You joined because you truly appreciated the combined force of intellectual energy created by the Guild. You know that it takes a lot more than just physical power to ascend to the zenith of (im)mortal living---an achievement you believe rests on the power of knowledge as well as the power of might. The Loremasters Guild rules more of Astyria than the commonwealth believe because without the technology constantly being improved by the Guild, everyone's lives would suffer. Unlike the Power Society, the Loremasters Guild understands that the importance of the group's existence is to further the cause of future generations, not forcing ridiculous tests onto its potential new members.

Any two members can induct a new member by conducting a one minute ceremony. (\emph{Roleplay accordingly.})

If there are four or more members in the Loremasters, any two members can eject an existing member by conducting a one minute ceremony \emph{over the target's unconscious (or dead) body}. (\emph{Roleplay accordingly.})

By virtue of membership in the Loremasters, you gain access to a pool of abilities. These abilities are shared across all Loremasters, including newly inducted members, so be careful with who you add to the society.

\begin{itemz}[Goals]
  \item Acquire as much information about everything forever!
  \item Keep the Loremasters Guild intact and dignified.
  \item Gain new members with great knowledge.
  \item Embarrass or otherwise weaken the Power Society by whatever means you desire.
  \item Ensure that whoever is the Supreme Command of the monsters is from the Loremasters (and certainly not from the Power Society).
\end{itemz}


\begin{members}[Members of the Guild attending this event.]
  \member{\cVampire{}} The vampire leader of the Guild. \cVampire{\They} is not very likeable, but the Guild has certainly risen in power since \cVampire{\they} took over.
	\member{\cGoblin{}} A sassy goblin with secrets. 
	\member{\cBabyFae{}} A winter fae who was inducted into the society for providing the group a handful of rare, ancient human wizard books.
	\member{\cSphinx{}} No one in the Loremasters Guild is sure whether or not \cSphinx{} is actually a member as no one has been able to decipher \cSphinx{\their} answer when asked.
	
\end{members}


\begin{itemz}[Ability Pool]
	\item \textbf{Research secret (3 uses per game) --} After conversing with a target for five minutes, you may learn a secret about them or their race.
	\item \textbf{Study ritual (2 uses per game) --} If you are shown the steps of a ritual, you can deduce its purpose and the consequences of completing it.
	\item \textbf{Etherialize (3 uses per game) --} Step lightly into the ethereal plane. You will appear to be a ghost. You can be seen and heard by anyone as usual, but you may only interact with other ethereal characters.
	\item \textbf{Forbidden words (1 use per game) --} Speak the unspeakable words of a long-forgotten ritual. You have only read but never spoken these words before, and have only vague hints as to what effect they might have. But it is clear that they should only be used in moments of desperation and may be especially dangerous to the speaker.
\end{itemz}
	


\end{document}
