\documentclass[blue]{guildcamp2}
\begin{document}

\name{\bPower{}}

\cenquote{``A truly strong person does not need the approval of others any more than a lion needs the approval of sheep.''}{-- Vernon Howard}

The Power Society is a hardy group of battletorn warriors who have fought their way to immense control over Astyria, both in politics and in brute force. The Power Society is run by the up and coming visionary known as \cRed{}. It is in a lifelong rivalry with the Loremasters Society.

The Society encourages its members to become as strong as possible. There is no discrimination as long as you can hold your own in a one on one battle. For obvious reasons, no weaklings are allowed to join; those members who work to gain presence in politics are still chosen by their physical prowess as well as mental. Each potential new member must pass a trial to prove their strength before the induction ritual into the Society. You and the strongest of your ancestors have always been members; you passed your trial with flying colors! The values of the Society are manifold, but you appreciate that the direction the Society has taken over the last fifty years has moved towards a more secret influence than in the past. You find the politics, while absolutely not your mug of ale, necessary for lasting power. The Loremasters Guild doesn't seem as if they have any real presence in Astyria because they mostly just shut themselves in the great Astyrian Library and ignore the world. You imagine every Loremasters member must never see the sun because they are always sitting bent over tomes. The Power Society doesn't mean as much to you as it did to your father, but you still participate fully in whatever tasks \cRed{} asks of you. You are a reliable member; you willingly use your strength to further the Society's goals for future generations. Once a member commits to joining, there is no abandoning the Society. Currently, the Master is \cRed{} who has fought many battles to protect his title. Many believe \cRed{} will take the Power Society to heights of influence unforeseen!

Any two members can induct a new member by conducting a one minute ceremony. They will typically have to have overpowered at least one worthy foe to be considered acceptable. (\emph{Roleplay accordingly.})

By virtue of membership in the Power Society, you gain access to a pool of abilities. These abilities are shared across all members, including newly inducted members, so be careful with who you add to the society.

\begin{itemz}[Goals]
  \item Acquire as much power and glory as possible!
  \item Keep the Power Society on top of every sniveling weakling.
  \item Gain new members with great power!
  \item Embarrass or otherwise weaken the Loremasters Society by whatever means you desire.
    \item Ensure that whoever is the Supreme Command of the monster army is from the Power Society (and certainly not from the pathethic Loremasters).
\end{itemz}


\begin{members} [Members of the Society attending this event.]
  \member{\cRed{}} The fearless draconic leader of the Society. \cRed{\They} is very agressive. \cRed{\They} is considered a visionary for advancing the Society's values.
	\member{\cMinotaur{}} A minotaur whose family has been solid loyal members since the founding of the Society. \cMinotaur{\Their} communication skills may be similar to that of a child, but no one can deny the strategic military genius \cMinotaur{\they} has brought to the Society and \cMinotaur{\their} own people.
	\member{\cLich{}} A sorcerous undead who has slaughtered any who dares to stand in \cLich{\their} way.
\end{members}

\begin{itemz}[Ability Pool]
	\item \textbf{Reveal Cowards (2 uses per game) --} Use on a target character to discover the exact and truthful status of their army, instead of whatever the scouts report.
	\item \textbf{The Scent of Treasure (2 uses per game) --} Receive a hint from the GM about the location of a specific treasure you are searching for. You may not receive the hint immediately. May be used at most once per character.
\item \textbf{Glory (3 uses per game) --} If you knock another player unconscious without direct assistance from any other character, gain +5CR for the next 30 minutes. This ability can only be used once per character.
	\item \textbf{Revenant (1 use per game) --} If you would die and you were killed by foes that outnumbered you, instead go ``not here'' and find a GM.  Your corpse is still on the ground and you will appear to be dead, but you will rise up again in five minutes. Note that if two members die simultaneously, the GM will choose who survives randomly.
\end{itemz}

\end{document}
