\documentclass[notebook]{guildcamp2} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nEzekiel{}}

\begin{page}{first}
This book describes a detailed set of procedures for resurrecting Ezekiel. The Oracle has already completed many of the necessary rituals and 
has provided you with the necessary reagents. Begin by finding a strong open flame such as a torch. Combine \iFlask{} and \iQuintu{}, destroying
\iQuintu{}. This will activate the flask.

When you complete this step, you may turn to \nbref{second}.
\end{page}

\begin{page}{second}
Ezekiel will be resurrected not in corporeal form, but by overlaying his spirit on top of an existing humanoid, although the nature of the magic
prevents the vessel from being a fae. The following races are acceptable vessels, roughly in order of preference: human, minotaur, goblin, troll, or ogre.

You can attempt to use another race as a vessel, although you are not certain how well the spell will work. The victim does not need to be a willing recipient, but their goals should still align with that of the fae.
As you interact with the other races at the council, you should be evaluating their suitability as recipients of Ezekiel's soul. Engage in a conversation of at least two minutes with members of two such races.

When you complete this step, with you may turn to \nbref{third}.
\end{page}

\begin{page}{third}
Now the hardest part, the one that The Oracle could not do for you: you must find the gemstone that was the centerpiece of Ezekiel's tombstone.
You know that it was stolen by the powerful lich \cLich{}, and is likely being used as a phylactery. You know that the phylactery must be near
the lich at all times, although is not likely to be on its person. Still it is likely well hidden.

When you find the phylactery, you may turn to \nbref{fourth} (it is okay if the phylactery has already been destroyed).
\end{page}


\begin{page}{fourth}
This gemstone contains Ezekiel's soul. To extract it, you must crush the phylactery and grind it into a powder, then pour it into the \iFlask{}. (If the phylactery has been destroyed, you just need to pour the powder into the flask.)

When you complete this step, you may turn to \nbref{fifth}.
\end{page}

\begin{page}{fifth}
The potion is now ready: whoever drinks it will obtain Ezekiel's will. Convince someone to drink the potion, preferably a human, minotaur, goblin, troll, or ogre. You may also force it upon someone who is Knocked Out or Restrained. When you complete this step, go find a GM.

Long live Ezekiel, Lord of the Fae!
\end{page}

\endnotebook

\end{document}
