\documentclass[notebook]{guildcamp2} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nmazeterpiece{}}

\begin{page}{first}
Rocks! Rocks! Rocks! All you have to work with is rocks! You hate how inflexible they are, but you love the appeal of using them for your mazes.
You need to show that Sphinx who is the boss around here. You need to hear about the best rocks in the world.

Turn the page after you have asked 5 other creatures at this conference what their favorite kind of rock is.
\end{page}

\begin{page}{second}
That didn't help. You need to figure this out. Spend 5 minutes in the dungeon searching for clues.

Turn the page once this is complete.
\end{page}

\begin{page}{third}

Hm. Yes. Progress. Finally. That is all very interesting, but you need traps in your mazes! Your mazes are legendary for their traps! Maybe those fae can give you some ideas? They trap humans all the time!

Turn the page after you have spend a total of 5 minutes talking to one or the other of the fae about traps.
\end{page}

\begin{page}{fourth}

Traps are always useful. You have some ideas for traps to put in your maze now.  Of course, you'll need to make sure that the Sphinx enters your maze. You know that the sphinx will refuse, having no respect for your cleverness. Find a partner who agrees to help you knock out the Sphinx and drag it to your maze.

Turn the page when you have found a willing ally. (Don't knock the sphinx out yet, you'd give away the game.)
\end{page}

\begin{page}{fifth}
Great. Now you can really do this. You just have to build your maze. You do this, of course, by sketching out your blueprints and using magic to will it into existence. But you forgot your sketching tools. Maybe someone around here has something you can use?

Turn the page after you have found a \iQuill{} or other game item that is clearly a writing implement, and a piece of \iPaper{}, and made a sketch of your maze.
\end{page}

\begin{page}{sixth}
Excellent. Spend 5 minutes standing at the entrance to your maze and willing it into existence. You may talk to other players, but not take any other actions. If you stop this action to do something else (like notice a waylay, engage in combat, etc.), you must start your 5 minutes over.

Turn the page after you have completed this task.
\end{page}

\begin{page}{seventh}
Excellent. Your masterpiece awaits! Now you need to get your ally and lure the Sphinx into a deserted area so you can knock it out and drag it to your maze! Then go find a GM.

Turn the page once the Sphinx has been trapped.
\end{page}

\begin{page}{eighth}
Congratulations. You have trapped the Sphinx! The Sphinx must complete your maze to escape and suffers a -5CR penalty until your puzzle has been solved!
\end{page}

\endnotebook

\end{document}
