\documentclass[notebook]{guildcamp2} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nraisemonster{}}

\begin{page}{first}
What makes a goblin like a human? Why can you raise only weak monsters? If you can figure out what makes a goblin and a human so similar, you may be able to isolate the ``monster'' element and study it. Maybe you need to extract the goblin's essence? 

Turn the page if you are able to do so.
\end{page}

\begin{page}{second}
So that's it. Hmm. What exactly is this? Maybe there is a book about it somewhere. 

Turn the page when you see the number 4321.
\end{page}

\begin{page}{third}
Ok, now you have the key knowledge---but you can't read it! What is this language? It is a language with pictorial symbols. Someone around here must know how to read this, but they cannot know what are you up to! They won't understand your genius.

Turn the page once the book has been translated.
\end{page}

\begin{page}{fourth}
Aha! The answer was right in front of your face! Of course that is the answer! Now you need to find a source that can amplify that ``beastly'' aspect in your ritual!

Turn the page after you have found this source.
\end{page}

\begin{page}{fifth}
Now you must test your hypothesis! If you can find a suitable corpse to raise, that would be the perfect experiment! It would be unwise to waste your experiment, on Onyx, in case it fails. Who around here is an adequate target?

Turn the page after you have performed your experiment.
\end{page}

\begin{page}{sixth}
You need to just add a few drops more and your ritual is perfected! Now you can be the most powerful necromancer in all of Aystyria! Congratulations.
\end{page}

\endnotebook

\end{document}
