\documentclass[notebook]{guildcamp2} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nriddletastic{}}

\begin{page}{first}
Numbers. Numbers. So many numbers are floating around your head! You need to find the best riddle, but how can you with so many numbers in your head? 

Turn the page when someone correctly answers one of your riddles.
\end{page}

\begin{page}{second}
What is the essence of existence? What is life? What is life to a monster? What is life to a human? If only you could find the human in disguise. Ask those around you ``What is the meaning of breathing to a dove?''

Turn the page when someone speaks for over 60 seconds in response to your question.
\end{page}

\begin{page}{third}
Now it is time that is driving you mad! What can you do to alleviate this mental soup that plagues your mind? Maybe you need to work this out through movement?

Turn the page when you have gotten three other creatures to hold hands with you in a circle (players may pretend to hold hands if you are not comfortable with physical contact) and then walk clockwise around that circle for 3 minutes. 

\end{page}
\begin{page}{fourth}
Numbers! Humans! Time! You have no idea where this riddle will come about! That dance was useless. You need inspiration! 

Turn the page when you have spoken to 5 other creatures for inspiration.
\end{page}

\begin{page}{fifth}
Ah! yes! Maybe that is the answer. You must go spend ten minutes alone, crafting this riddle to defeat the Minotaur!

Turn the page after you have done this.
\end{page}

\begin{page}{sixth}
Yes! This is it! Now you must go and place two \iBilberries{} and four \iEyebright{} into a cauldron. Stir for 60 seconds while incanting your riddle: ``What walks on four legs in the morning, two legs in the afternoon, and three legs in the evening?'' (A human)

After you have created this potion, you must force it down the throat of that blasted minotaur! You know that \cMinotaur{} will never cooperate whilst conscious! Afterwards, turn the page.
\end{page}

\begin{page}{seventh}
After the potion has been poured down the throat of the knocked out minotaur, the minotaur must answer the riddle (You will need to tell \cMinotaur{\them} the riddle). The Minotaur suffers a -5CR penalty until the riddle is solved. 
\end{page}


\endnotebook

\end{document}
