\documentclass[notebook]{guildcamp2} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nspeaknormal{}}

\begin{page}{first}
\end{page}

\begin{page}{first}
You wish to speak the common language of the people and monsters. How do you do so? Perhaps you need to listen to their vernacular? Pose the question ``What have you done the day before yesterday's tomorrow's tomorrow?'' to every creature you see until you receive an answer that mentions something they have done today.

Turn the page when you receive a proper answer.
\end{page}

\begin{page}{second}
Hm. That was quaint. Are you sure you want this? Yes. Yes you are. Listening isn't your style, though it did help a little. Maybe you need to read one of their books?

Turn the page when you find a book with the word ``common'' in the title and read it.
\end{page}

\begin{page}{third}
Well, that was only a little bit helpful. Maybe you need a spell? Or a wish? Yes, a wish!

Turn the page after you have seen a magic user (a Fae, a Djinni, a Demon or a Lich) about your wish. 
\end{page}

\begin{page}{fourth}
Well, that was unfortunately not productive. Maybe the potion idea was right, after all? You'd think that you would know how to make a potion to solve this, but it seems that knowledge is beyond you! That demon, \cDemon{} or the old dragon \cOnyx{} might know something.

Turn the page after you have asked one or the other about this potion idea.
\end{page}

\begin{page}{fifth}
Yes! A potion exists! But how can you obtain it? Where could it be? You go into a trance and sense that it is near---surrounded by stone?

Deck a hand of 3 and then go find a GM.

Turn the page after you have obtained the potion.
\end{page}

\begin{page}{sixth}
Wow. What a long journey it has been to obtain this potion! Now you will hopefully gain what you desire! You drink the potion and gain the ability to speak in simple mundane phrases. Congratulations?
\end{page}

\endnotebook

\end{document}
