%%%%%
%%
%% This file sets up the Abil datatype and creates Abil macros.  These
%% are for abilities that characters may have.
%%
%%%%%

\DECLARESUBTYPE{Abil}{Element}
\PRESETS{Abil}{
  \F\MYtext	%% text of ability, read by user
  \F\MYeffect	%% effect text of ability, read by recipient(s)
  }


%%%%%
%% \ability{<name>}{<text>}{<effect>}
%%
%% \ability is a wrapper around \INSTANCE, useful for 1-shot abilities,
%% etc.
\newinstance{Abil}{\ability[3]}{
  \s\MYname{#1}\s\MYtext{#2}\s\MYeffect{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Abil}{\aTest}{
  \s\MYname	{Test Ability}
  \s\MYtext	{You are a test.}
  \s\MYeffect	{This is a Test.}
  }

\NEW{Abil}{\aSpecial}{
  \s\MYname	{Special Powers}
  \s\MYtext	{You have special powers, as detailed in your \gTest{}
		greensheet.}
  \s\MYeffect	{I have special powers!}
  \s\MYgreens	{\gTest{}}
  \suite
  }

\NEW{Abil}{\aRegeneration}{
  \s\MYname	{Regeneration}
  \s\MYtext	{You can only be killed if you are wounded or killing blowed using fire. If you are wounded with no use of a fire weapon, you enter the ``Knocked Out'' state and regenerate health for 5 minutes, after which you wake up as normal. If anyone uses a wound or  killing blow on you that does not involve fire, it appears to the other character that they have succeeded (play dead), but you are in fact only knocked out.}
  \s\MYeffect	{The wounds seem to be closing up!}
  }
	
\NEW{Abil}{\aShapeshifting}{
  \s\MYname	{Tear of Magic}
  \s\MYtext	{You have a +10 defensive CR as long as you possess a \iTearofMagic{}. If you lose the item, this ability does not process, but if you acquire a new Tear, you may once again use this ability.}
  \s\MYeffect	{This person's form shifts into a small animal, he/she ignores your attack}
  }
	
\NEW{Abil}{\aImpenetrableScales}{
  \s\MYname	{Impenetrable Scales}
  \s\MYtext	{You can only be killed by use of a specific legendary sword known as the Sword of Ice! If you would be wounded by any other means, instead you go ``Not Here'' and spend the next 5 minutes regenerating.}
  \s\MYeffect	{You cannot defeat me! I fly away with anger in my eyes.}
  }
	
\NEW{Abil}{\aBattleRage}{
  \s\MYname	{Battle Rage}
  \s\MYtext	{If you are being wounded by an attack that you cannot normally resist, resist it freely. For the next 1 minute, you get +10 CR. After this duration, you are fatigued and enter the ``Knocked Out'' state. Wake up in 5 minutes healthy. This ability has a 30 min cool down.}
  \s\MYeffect	{Your attack bounces off and you see my eyes glow red.}
  }
	
\NEW{Abil}{\aBlink}{
  \s\MYname	{Teleport}
  \s\MYtext	{If you are attacked, you may go ``Not Here'' instead of being hit. Any time in the next 5 minutes, you may come back into game at any location in gamespace by switching your badge back. If you are waylaid, you cannot use this ability.}
  \s\MYeffect	{Just as you were about to strike, your foe vanishes!}
  }
	
\NEW{Abil}{\aAbyss}{
  \s\MYname	{Hell Fire}
  \s\MYtext	{If you would be knocked out or wounded you may immediately make a knock out attack of CR 15 on everyone within 1 zones of control. This ability has a 1 hour cool down.}
  \s\MYeffect	{Just as you were about to strike, a blast of dark fire shoot forth}
  }
  
\NEW{Abil}{\aTamper}{
  \s\MYname	{Seduce Scout}
  \s\MYtext	{Up to 3 times in game, you may dispatch a succubus to go seduce a scout. This allows you to modify the reports coming in about army movements. You may make any army (including your own) appear to be in one of the following states: Committed to Monster Army, Committed to Human Army, or Seeking Asylum with the Humans. This effect will last for 15 minutes, after which a new scout will report the true movements of the Army  (you may chain uses of this ability to continue obfuscating Army movements). When you activate this ability, tell a GM which Army you want reported in what state.}
  \s\MYeffect	{No effect.}
  }
	
\NEW{Abil}{\aSmokeBomb}{
  \s\MYname	{Now You See Me}
  \s\MYtext	{If you would be attacked you may throw a Smoke Bomb, this consumes it, tear up the item card. You spend the next 5 minutes ``Not Here'', renter game in any room you have already visited.}
	\s\MYeffect	{*Cough* Where did your enemy go?! *Cough* And why is there so much smoke?!}
  }
	
\NEW{Abil}{\aPhylactery}{
  \s\MYname	{Phylactery}
  \s\MYtext	{As long as your phylactery is intact, you cannot be permanently killed. If you would be killed by normal mechanics (bleed out from wound, killing blow, etc) you body disintegrates into nothing, but your spirit endures. Go ``Not here'' and reform in a separate room of your choice in gamespace. If your phylactery is destroyed, this ability no longer processes and you can be killed as normal.}
  \s\MYeffect	{An unimpressed expression forms on my face as I disintegrate into the ground.}
  }
	
\NEW{Abil}{\aBloodBank}{
  \s\MYname	{Blood Bank}
  \s\MYtext	{Using all the stored blood you have you may return from death once. Pretend to be dead for up to 30 minutes, and when you choose, return to game in the spot where you where struck down.}
  \s\MYeffect	{The Vampire's eyes fill with life as it rises from the dead}
  }

\NEW{Abil}{\aRiddleMeThis}{
  \s\MYname	{Riddle Me This!}
  \s\MYtext	{You have a +10 defensive CR}
  \s\MYeffect	{It's eyes they are so hypnotic}
  }
\NEW{Abil}{\aHealer}{
  \s\MYname	{Healer}
  \s\MYtext	{You must touch (OOC ask permission first, or just pretend) the intended wounded target for three minutes (this stops their bleed out timer), after which they become knocked out for the remaining time they would be wounded. This ability can be interrupted.}
  \s\MYeffect	{This person is applying first aid though magic. This ability can be interrupted.}
  }
\NEW{Abil}{\aBagofHolding}{
  \s\MYname	{Bag of Holding}
  \s\MYtext	{You may hold and hide without physically holding 1 hand bulky worth of items. The item you are storing can still be found in a full body search.}
  \s\MYeffect	{I have a small pocket dimension perfect for stolen goods}
  }
	
\NEW{Abil}{\aStoneGaze}{
  \s\MYname	{Stone Gaze}
  \s\MYtext	{When you make a dark water attack, instead of ``knock out'' or ``wound'', you may turn someone to stone for 5 minutes instead. The target is invulnerable to further attacks, searches ,or killing blows for this time.}
  \s\MYeffect	{You are turn to stone for 5 minutes. You are now a statue and  cannot be targeted by attacks, killing blows, or searches.}
  }
%% Basic DarkWater-style Martial Attack abilities


%% Everyone has these 3
\NEW{Abil}{\aAssist}{
  \s\MYname	{Assist}
  \s\MYtext	{You can assist someone else's attack.  You must be
		within ZoC of both the attacker and target.  Within two
		seconds of an attack, direct this at the attacker,
		saying ``\MYname'' and your CR.}
  \s\MYeffect	{I assist your attack.}
  }

\NEW{Abil}{\aKnockOut}{
  \s\MYname	{Knock Out}
  \s\MYtext	{You can knock someone out as an attack.  Say ``\MYname'' and your CR.}
  \s\MYeffect	{I knock you out.}
  }

\NEW{Abil}{\aWound}{
  \s\MYname	{Wound}
  \s\MYtext	{You can wound someone as an attack.  Say ``\MYname'' and
		your CR.}
  \s\MYeffect	{I wound you.}
  }


%% the \basecombat macro can be prepended to the Char abils list
%% (in char-LIST.tex)
\def\basecombat{\aKnockOut{}\aWound{}\aAssist{}}


%% only some people have these
\NEW{Abil}{\aDisarm}{
  \s\MYname	{Disarm}
  \s\MYtext	{You can disarm one item from someone as an attack.  Say
		``\MYname'' and your CR.  Point at the item you want to
		disarm.  If the attack works, they must drop that item.}
  \s\MYeffect	{I disarm that item.}
  }

\NEW{Abil}{\aRestrain}{
  \s\MYname	{Restrain}
  \s\MYtext	{You can restrain someone as an attack.  Say ``\MYname''
		and your CR.  You may freely drag, attack, or (if you have
		a weapon) killing-blow them.  To do anything else, or if
		your health state changes, incant ``release'' and let them
		go.}
  \s\MYeffect	{I restrain you.  You are restrained until I incant
		``release.''}
  }

\NEW{Abil}{\aThrow}{
  \s\MYname	{Throw}
  \s\MYtext	{You can throw someone as an attack.  Say ``\MYname'' and
		your CR.  Point in the direction you want to throw them.}
  \s\MYeffect	{I throw you.  Go in the direction I point ten full steps
		or until you hit a wall or similar.}
  }
	
	\NEW{Abil}{\aBloodlust}{
		\s\MYname {Blood Lust}
		\s\MYtext {When you point at a player, you can inspire bloodlust in them and they will attack the nearest creature aside from you until either the creature is dead or they are dead or knocked out. You can use this ability once every 5 minutes.}
		\s\MYeffect {You have an uncontrollable urge to kill the nearest creature other than me. Attack them until they are dead or you are dead or knocked out.}
}
	\NEW{Abil}{\aFirebreath}{
		\s\MYname {Firebreath}
		\s\MYtext {You can choose to make your attacks count as flame attacks}
		\s\MYeffect {You breath fire on your target. This does standard CR damage as a fire attack. You can also use this as a light source.}
		}
		
	\NEW{Abil}{\aNegotiate}{
		\s\MYname {Influence with Humans}
		\s\MYtext {If you accompany another army leader down The Windy Corridor and they show you a missive they are dispatching to make peace with the humans, you can use your influence to help or hurt their case. Draw a circle on the back of a missive to make the asylum request more likely to succeed. Draw a triangle on the back of a missive to make the asylum request more likely to fail.}
		\s\MYeffect {I can influence missives dispatched to humans. Instead of seeking asylum, you also have the option to commit your forces to help the human army.}
		}
		
	\NEW{Abil}{\aBetrayal}{
		\s\MYname {Betrayal of your own kind}
		\s\MYtext {This is a one time use ability granted to you by your God to sow the seeds of war, chaos and destruction. If you accompany another army leader down the Windy Corridor and they show you a missive they are dispatching to commit to the Monster army, you may draw a star on the back of the missive to indicate that this army is imbued with the power of betrayal. Have the leader write the name of the faction they wish to betray next to the star.}
		\s\MYeffect {You may commit your forces to betraying another army. Neither your forces nor theirs will contribute to the Monster army in the battle to come, and the betrayed army will be decimated.}
		}
		
		\NEW{Abil}{\aCommitForces}{
		\s\MYname {Dispatch Forces or Request Asylum}
		\s\MYtext {You command a great army. By going to The Windy Corridor, you can choose to either dispatch them to assist the other monster forces arranging to oppose the human army, or sneak around the monster army and request asylum from the humans. All commitments are final unless you know otherwise.}
		\s\MYeffect {I am writing a missive to my army.}
		}
		
		\NEW{Abil}{\aFakeCommit}{
		\s\MYname {Astral Illusion}
		\s\MYtext {You can create an illusion on the astral plane where the Djinni live. To the untrained eye, it will look like the Djinni forces have been dispatched (the monster army is unable to easily survey the Djinni's home on the astral plane). To do this, write a missive to the Djinni army at the end of The Windy Corridor.}
		\s\MYeffect {I am meditating.}
		}
		
		\NEW{Abil}{\aSleepingDust}{
		\s\MYname {Deep Slumber}
		\s\MYtext {You can call upon the forces of the earth to force another character to sleep. Perform a four-second Waylay on another character and exclaim ``Somnus!'' in a clear voice. They may not be engaged in combat at the time. If you convince someone to willingly fall asleep, you may freely use this ability.}
		\s\MYeffect {You suddenly feel exhausted and are now Knocked Out. You will not remember what caused you to fall asleep.}
		}
		
		\NEW{Abil}{\aReadDreams}{
		\s\MYname {Read Dreams}
		\s\MYtext {You are an expert at reading and interpreting the dreams of others. To read someone's dreams, they must be Knocked Out or Wounded. Hold your dreamcatcher over their head for ten seconds then use this ability on them.}
		\s\MYeffect {You must describe what you are dreaming about (you are most likely dreaming about something you loathe or love, or your hopes and fears regarding one of your goals at this council). If you are a human, you must reveal it to me.}
		}
		
		\NEW{Abil}{\aControlDreams}{
		\s\MYname {Control Dreams (Humans only)}
		\s\MYtext {You have spent centuries mastering the magic needed to read and control human dreams. You can manifest yourself within their dreams, and even change their dreamscapes entirely. You are working on controlling monster dreams too, but cannot do so yet. To control someone's dreams, you must first use your Read Dream ability. Then describe what they are now dreaming about instead. They will interpret this as an omen.}
		\s\MYeffect {You are now experiencing the dream I am describing. If this dream describes past or future events at this council, you believe this is likely the way things did or will happen, unless you have reason to believe otherwise.}
		}
		
		\NEW{Abil}{\aFly}{
			\s\MYname {Fly}
			\s\MYtext {This ability allows you to fly}
			\s\MYeffect {If a mechanic specifically limits access to people who can fly, you have access.}
			}
			
			\NEW{Abil}{\aForge}{
				\s\MYname {Forge}
				\s\MYtext {You can reforge broken weapons in the Golem Lab}
				\s\MYeffect {If you have  four pieces of a broken weapon, you may reforge it by getting a level 3 hand in decking in the Golem Lab. If you do so, tell a GM.}
				}
		
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
