%%%%%
%%
%% This file creates the Item, ItemPacket, ItemFold, ItemEnvelope, and
%% ItemLabel datatypes, and creates macros for each.  These are for
%% various types of in-game items.
%%
%%%%%


%%%%%
%% Item macros are for normal item cards.
\DECLARESUBTYPE{Item}{TransElement}
\PRESETS{Item}{
  \FD\MYtext	{} %% longer text of item
  \FD\MYmark	{} %% possible contents of shaded ``mark'' on card
  \FD\MYbulky	{0} %% potential bulkiness
  \FD\MYcapacity{N/A} %% potential capacity
  \sd\MYlistmap	{\item\MYname\ifx\MYnumber\empty\else\ (\MYnumber)\fi}
  }


%%%%%
%% \prop
%% \unstash
%% \bulky{<number>}
%% \contain{<number>}
%%
%% \prop inside an Item macro labels the card as a prop.  \unstash
%% labels the card as unstashable.  \bulky{n} labels the card as
%% n-hands bulky.  \contain{n} labels the card with n-hands capacity.
\def\prop{%
  \append\MYmark{ ~PROP~ }}
\def\unstash{%
  \append\MYmark{ ~UNSTASHABLE~ }}
\def\bulky#1{%
  \s\MYbulky{#1}%
  \append\MYmark{\mbox{ ~\MYbulky-Hand~Bulky~ }}}
\def\contain#1{%
  \s\MYcapacity{#1}%
  \append\MYmark{\mbox{ ~\MYcapacity-Hand~Capacity~ }}}


%%%%%
%% ItemPacket macros are for item cards with an attached packet.
%% They are a subtype of Item.
\DECLARESUBTYPE{ItemPacket}{Item}
\PRESETS{ItemPacket}{
  \F\MYcontents
  }


%%%%%
%% ItemFold macros are for items represented by just a folded packet.
%% They are a subtype of ItemPacket, with the longer text and ``mark''
%% left blank, since they have no actual item card.
\DECLARESUBTYPE{ItemFold}{ItemPacket}
\PRESETS{ItemFold}{
  \s\MYmark{}
  }


%%%%%
%% ItemEnvelope macros are for items represented by just an envelope.
%% They are a subtype of ItemPacket, with the longer text and ``mark''
%% left blank, since they have no actual item card.
\DECLARESUBTYPE{ItemEnvelope}{ItemPacket}
\PRESETS{ItemEnvelope}{
  \s\MYmark{}
  }


%%%%%
%% ItemLabel macros are for small labels that would get used on
%% physreps, e.g. gun labels.  The ``mark'' is left blank, since
%% it isn't used for these.
\DECLARESUBTYPE{ItemLabel}{Item}
\PRESETS{ItemLabel}{
  \s\MYmark{}
  }


%%%%%
%% \icard[<extras>]{<name>}{<number>}{<text>}
%% \specialicard[<extras>]{<name>}{<number>}{<text>}{<mark>}
%% \itempacket[<extras>]{<name>}{<number>}{<text>}{<mark>}{<contents>}
%% \itemfold{<name>}{<number>}{<text>}{<contents>}
%% \itemenvelope{<name>}{<number>}{<text>}{<contents>}
%% \itemlabel{<name>}{<number>}{<text>}
%%
%% These are wrappers around \INSTANCE, useful for 1-shots.
%%
%% For \icard, \specialicard, and \itempacket, the optional <extras>
%% (in []'s) is for things like \unstash and \bulky{3}.  For example,
%% \icard[\prop\contain{2}]{..}{..}{..}{..} gives an item that has a
%% prop and 3-hands capacity.
%%
%% The last arg (#5) to \specialicard is for anything extra you may
%% want in the ``mark''
\newinstance{Item}{\icard[4][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}#1}
\newinstance{Item}{\specialicard[5][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}\s\MYmark{#5}#1}
\newinstance{ItemPacket}{\itempacket[6][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}\s\MYmark{#5}\s\MYcontents{#6}#1}
\newinstance{ItemFold}{\itemfold[4]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}\s\MYcontents{#4}}
\newinstance{ItemEnvelope}{\itemenvelope[4]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}\s\MYcontents{#4}}
\newinstance{ItemLabel}{\itemlabel[3]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Item}{\iTest}{
  \s\MYname	{Test Item}
  \s\MYnumber	{0000}
  \s\MYtext	{A Test Item Card}
  }

\NEW{ItemPacket}{\iTestPacket}{
  \s\MYname	{Test Item}
  \s\MYnumber	{0000}
  \s\MYtext	{A Test Item with a big red button.  Open packet if
		you press the big red button.}
  \s\MYcontents	{The item beeps at you.}
  }

\NEW{ItemFold}{\iTestFold}{
  \s\MYname	{Test Food}
  \s\MYnumber	{0000}
  \s\MYtext	{open if you eat}
  \s\MYcontents	{It tastes yummy.}
  }

\NEW{Item}{\iQuill}{
  \s\MYname	{The Quill of Dark Desire}
  \s\MYnumber	{365	}
  \s\MYtext	{A Quill that emanate  magical energy}
  }

\NEW{ItemFold}{\iTestEnvelope}{
  \s\MYname	{Test Food}
  \s\MYnumber	{0000}
  \s\MYtext	{open if you eat}
  \s\MYcontents	{It tastes yummy.}
  }

\NEW{ItemLabel}{\iTestLabel}{
  \s\MYname	{Test Gun Label}
  \s\MYnumber	{0000}
  \s\MYtext	{Disc gun, loadable to 20 shots.}
  }

\NEW{Item}{\iWhatzit}{
  \s\MYname	{Whatzit}
  \s\MYnumber	{12345}
  \s\MYtext	{If you press it, open packet a.  If you twirl it, open
		packet b.  If you pull it, open packet c.}
  \bulky	{1}
  \s\MYsigns	{\signstrip{a}{it goes ``beep.''}
		\signstrip{b}{it goes ``whoop.''}
		\signstrip{c}{it goes ``bang.''}
		}
  \s\MYabils	{\ability{Stop Crying}{By futzing with the Whatzit, you
		can make babies stop crying.}{I make the baby stop
		crying.}
		}
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\NEW{Item}{\iDaywalkerFruit}{
  \s\MYname	{Sunberries}
  \s\MYnumber	{162}
  \s\MYtext	{These grow on sunny hillsides and are harvested at Midsummer.}
  } %exists

\NEW{Item}{\iEyebright}{
  \s\MYname	{Eyebright}
  \s\MYnumber	{982}
  \s\MYtext	{A small, many-petaled white flower with a bright yellow center.}
  } %exists

 \NEW{Item}{\iPhylacterydust}{
  \s\MYname	{Phylactery Dust}
  \s\MYnumber	{375}
  \s\MYtext	{A fine glowing powder}
  } %exists
 
\NEW{Item}{\iDreamcatcher}{
  \s\MYname	{Dreamcatcher}
  \s\MYnumber	{822}
  \s\MYtext	{An intricate jade talisman engraved with a starry landscape.}
  } %exists, put with baby fae

	%\NEW{Item}{\iQuill}{
  %\s\MYname	{The Quill of Dark Desire}
  %\s\MYnumber	{0000}
  %\s\MYtext	{A Quill that emanate  magical energy}
  %}
\NEW{Item}{\iGingko}{
  \s\MYname	{Gingko Leaves}
  \s\MYnumber	{234}
  \s\MYtext	{Green and yellow fan-shaped leaves.}
  } %exists
\NEW{Item}{\iBaster}{
	\s\MYname {Turkey Baster}
	\s\MYnumber {264}
	\s\MYtext {It bastes turkeys.}
	} %exists
	
\NEW{Item}{\iBilberries}{
  \s\MYname	{Bilberries}
  \s\MYnumber	{847}
  \s\MYtext	{Small, dark blue berries that resemble blueberries.}
  }%exists
  
\NEW{Item}{\iBlueprint}{
  \s\MYname	{Magical Gun Blueprints}
  \s\MYnumber	{434}
  \s\MYtext	{Meticulously-drafted blueprints of how to augment a human gun with magically-enhanced propulsion.}
  } %exists, put with wizard
  
  \NEW{Item}{\iForsythia}{
  \s\MYname	{Forsythia}
  \s\MYnumber	{347}
  \s\MYtext	{A cluster of bright yellow flowers.}
  } %exists
  	
\NEW{Item}{\iSwordofIce}{
  \s\MYname	{The Legendary Sword of Ice}
  \s\MYnumber	{249}
  \s\MYtext	{You feel a surge of power while holding this sword. +5 CR while weilding this item.}
  \s\MYbulky	{2}
  } %exists
	
\NEW{Item}{\iVorpalSwordofWonder}{
  \s\MYname	{Sword fragment}
  \s\MYnumber	{123}
  \s\MYtext	{You feel a tingling sensation as you touch this fragment.}
  \s\MYbulky	{1}
  } %exists
\NEW{Item}{\iRVorpal}{
	\s\MYname {Vorpal Sword of Wonder}
	\s\MYnumber {321}
	\s\MYtext {The reforged Vorpal Sword of Wonder! It glows brightly, with a razor sharp blade.}
	}
	
\NEW{Item}{\iOrbofPower}{
  \s\MYname	{The Legendary Orb of Power}
  \s\MYnumber	{281}
  \s\MYtext	{This orb radiates with heat and magic. You may treat your cr as 15  long as you possess the orb.}
  \s\MYbulky	{1}
  } %exists
	
	\NEW{ItemFold}{\iTearofMagic}{
  \s\MYname	{Tear of Magic}
  \s\MYnumber	{303}
  \s\MYtext	{open if you consume}
  \s\MYcontents	{Go see a GM}
  } %exists. both fae have
	
\NEW{Item}{\iSeedoftheWorldTree}{
  \s\MYname	{Seed of the World Tree}
  \s\MYnumber	{605}
  \s\MYtext	{A glowing seed of the World Tree}
  } %exists
\NEW{Item}{\iPhylactery}{
  \s\MYname	{Phylactery}
  \s\MYnumber	{403}
  \s\MYtext	{A glowing gemstone. You may destroy this item by making a combined CR 20 attack against it. If you do so, go ``Not here'' and bring this item to a GM as soon as possible. %goes in the krogoth's room
	} %exists
  }
  
\NEW{Item}{\iLovePotion}{
  \s\MYname	{The Love Potion}
  \s\MYnumber	{203}
  \s\MYtext	{A pink potion that smells nice %goes in the river
	}
  } %exists
  
\NEW{Item}{\iSpeakPotion}{
  \s\MYname	{A Blue Potion}
  \s\MYnumber	{204}
  \s\MYtext	{A blue potion that swirls and sparkles. %GM has
	}
  }
  
\NEW{Item}{\iHolyBook}{
	\s\MYname {Holy Book of Groznak}
	\s\MYnumber {111}
	\s\MYtext {A book sacred to the followers of The God of War. A magical force protects the book from being touched. \emph{You may not interact with this object unless you know otherwise.}}
	} %exists
	
\NEW{Item}{\iRitualWand}{
	\s\MYname {The Ritual Wand}
	\s\MYnumber {222}
	\s\MYtext {A wand that glows}
	\s\MYbulky	{1}
	} %exists
	
\NEW{Item}{\iReaperIdol}{
	\s\MYname {Idol of the Reaper}
	\s\MYnumber {666}
	\s\MYtext {A statue of the grim reaper. The holder and any group they're in my pass through the warded door in the dungeon.}
	\s\MYbulky	{1}
	} %exists
	
\NEW{Item}{\iDominationIdol}{
	\s\MYname {Idol of Domination}
	\s\MYnumber {777}
	\s\MYtext {A statue of a pile of chains. The holder and any group they're in my pass through the warded door in the dungeon.}
	\s\MYbulky	{1}
	} %exists
	
\NEW{Item}{\iNatureIdol}{
	\s\MYname {Idol of Nature}
	\s\MYnumber {811}
	\s\MYtext {A statue of a tree. The holder and any group they're in my pass through the warded door in the dungeon.}
	\s\MYbulky	{1}
	} %exists
	
\NEW{Item}{\iDagger}{
	\s\MYname {Sacrificial Dagger}
		\s\MYnumber {148}
	\s\MYtext {A dagger used for ritual sacrifices. It bears the mark of the God of War. A magical force protects the dagger from being touched. \emph{You may not interact with this object unless you know otherwise.}}
	} %exists
	
\NEW{Item}{\iWardBook}{
	\s\MYname {Ward and Rune Repair Manual}
	\s\MYnumber {694}
	\s\MYtext {A book containing instructions on repairing wards and runes}
	} %exsists
	
\NEW{Item}{\iRope}{
	\s\MYname {Rope}
	\s\MYnumber {250}
	\s\MYtext {A coil of rope}
	} %exists
	
\NEW{Item}{\iTorch}{
	\s\MYname {Torch}
	\s\MYnumber {352}
	\s\MYtext {A burning torch. It is a good light source.}
	} %exists
\NEW{Item}{\iSmokeBomb}{
	\s\MYname {Smoke Bomb}
	\s\MYnumber {215}
	\s\MYtext {A small glass orb filled with a dark liquid. Consume upon use requires ablity}
	} %exists
		
\NEW{Item}{\iNightshade}{
	\s\MYname {Nightshade}
	\s\MYnumber {658}
	\s\MYtext {A curious looking white and purple flower}
	} %exists
	
\NEW{Item}{\iBHeart}{
	\s\MYname {Bleeding Heart}
	\s\MYnumber {199}
	\s\MYtext {A curious looking red and pink flower}
	} %exists
	
\NEW{Item}{\iCandle}{
	\s\MYname {Candle}
	\s\MYnumber {098}
	\s\MYtext {A plain, wax candle. It is a good light source.}
	}
\NEW{Item}{\iBCandle}{
	\s\MYname {Black Candle}
	\s\MYnumber {097}
	\s\MYtext {A candle made from pitch black wax, as far as you can tell. When lit, it seems to suck in light instead of providing it.}
	} %exists

	\NEW{Item}{\iStorch}{
		\s\MYname {Sacred Torch}
		\s\MYnumber {373}
		\s\MYtext {A torch that burns with a magical flame. Not only does it provide light, but attacks made with it count as fire damage. It also counts as three torches for the purposes of having multiple light sources or sources of fire.}
		} %exists
	
\NEW{Item}{\iCFungus}{
	\s\MYname {Cave Fungus}
	\s\MYnumber {512}
	\s\MYtext {A clump of mushrooms taken from a cave.}
	}%exists

\NEW{Item}{\iCFirearm}{
	\s\MYname {Stealthy Firearm}
	\s\MYnumber {556}
	\s\MYtext {A gun which gives you +5 CR when used. You must you the incant bang when using the Stealthy Firearm}
	}%exists
	
\NEW{Item}{\iKeyT}{
	\s\MYname {Key to Treasure Room}
	\s\MYnumber {558}
	\s\MYtext {This is a big, golden key that unlocks Onyx's treasure room.}
	}%exists
	
\NEW{Item}{\iGolemNotesA}{
	\s\MYname {Zumwalt's Golem Construction Manual, Part 1}
	\s\MYnumber {991}
	\s\MYtext {This is a torn set of pages that describe how to build a golem, and appears to be a part of a larger work. The writing style is very unusual: it does not appear to be hand-written.}
	} %exists

\NEW{Item}{\iGolemNotesB}{
	\s\MYname {Zumwalt's Golem Construction Manual, Part 2}
	\s\MYnumber {992}
	\s\MYtext {This is a torn set of pages that describe how to build a golem, and appears to be a part of a larger work. The writing style is very unusual: it does not appear to be hand-written.}
	} %cannot find
	
\NEW{Item}{\iGolemNotesC}{
	\s\MYname {Zumwalt's Golem Construction Manual, Part 3}
	\s\MYnumber {993}
	\s\MYtext {This is a torn set of pages that describe how to build a golem, and appears to be a part of a larger work. The writing style is very unusual: it does not appear to be hand-written.}
	} %exitst

\NEW{Item}{\iGolemNotesD}{
	\s\MYname {Zumwalt's Golem Construction Manual, Part 4}
	\s\MYnumber {994}
	\s\MYtext {This is a torn set of pages that describe how to build a golem, and appears to be a part of a larger work. The writing style is very unusual: it does not appear to be hand-written.}
	} %cannot find
	
\NEW{Item}{\iGolemNotesE}{
	\s\MYname {Zumwalt's Golem Construction Manual, Part 5}
	\s\MYnumber {995}
	\s\MYtext {This is a torn set of pages that describe how to build a golem, and appears to be a part of a larger work. The writing style is very unusual: it does not appear to be hand-written.} %exists
	}
	
\NEW{Item}{\iGolemControlRod}{
	\s\MYname {An Ornate Rod}
	\s\MYnumber {490}
	\s\MYtext {This steel rod is engraved with complicated, glowing runes. The word \textbf{Zumwalt} is engraved on the handle.}
	} %exists
	
	\NEW{Item}{\iDemonomicron}{
  \s\MYname	{Demonomicron}
  \s\MYnumber	{667}
  \s\MYtext	{An old book bound in leather. Inside lies the history Demonkind written in a magical language.}
  }
	
\NEW{Item}{\iSphinxBook}{
  \s\MYname	{Common Children's Tales}
  \s\MYnumber	{4}
  \s\MYtext	{A weathered book with human cautionary tales.}
	}
	
  \NEW{Item}{\iLichBook}{
	\s\MYname {Physiology and Evolution of the Magical Beast}
	\s\MYnumber {4321}
	\s\MYtext {This is a book. It is filled with a magical symbolic language that you cannot read. }
	} %exists
	
\NEW{Item}{\iAncientSorcery}{
	\s\MYname {Voynich Manuscript}
	\s\MYnumber {291}
	\s\MYtext {This is an ancient tome of sorcerous knowledge. If you are a sorcerer or, a species predisposed to sorcery (Lich, Vampire, Djinni, Demon, Basilisk), as long as you have this book on your person, your CR is +5.}
	}
	
\NEW{Item}{\iMissive}{
	\s\MYname {Missive to dispatch an army}
	\s\MYnumber {100}
	\s\MYtext {
	
  I, \underline{\hspace*{3cm}}, the leader if the \underline{\hspace*{3cm}} army, order my forces:
  
	
	\emph{(Choose one)}
	
	\begin{itemize}
	\item To join with the monster horde and oppose the humans!
	\item To leave the other monsters to their fate and seek asylum with the humans!
	\end{itemize} %exists
	}
	}
	
	\NEW{Item}{\iFlask}{
  \s\MYname	{Flask of Spiritual Resurrection}
  \s\MYnumber	{706}
  \s\MYtext	{A foul-smelling flask containing a brew that combines a powerful set of reagents.}
  }
	
	\NEW{Item}{\iQuintu}{
  \s\MYname	{A Quintu Seed}
  \s\MYnumber	{952}
  \s\MYtext	{One of the most powerful fruits from the heart of the fae realms.}
  }
	\NEW{Item}{\iPaper}{
	\s\MYname {Paper}
	\s\MYnumber {265}
	\s\MYtext {A plain sheet of paper}
	}
	\NEW{Item}{\iNormalQuill}{
	\s\MYname {Quill}
	\s\MYnumber {724}
	\s\MYtext {A regular quill used for writing}
	}
	
	
	
%%Souls
\NEW{Item}{\iOnyxSoul}{
	\s\MYname {Soul of a Black Dragon}
	\s\MYnumber {}
	\s\MYtext {The soul of a Black Dragon. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iRedSoul}{
	\s\MYname {Soul of a Red Dragon}
	\s\MYnumber {}
	\s\MYtext {The soul of a Red Dragon. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iHumanSoul}{
	\s\MYname {Soul of a Human}
	\s\MYnumber {}
	\s\MYtext {The soul of a Human. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iVampireSoul}{
	\s\MYname {Soul of a Vampire}
	\s\MYnumber {}
	\s\MYtext {The soul of a Vampire. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iSphinxSoul}{
	\s\MYname {Soul of the Sphinx}
	\s\MYnumber {}
	\s\MYtext {The soul of the Sphinx. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iDemonSoul}{
	\s\MYname {Soul of a Demon}
	\s\MYnumber {}
	\s\MYtext {The soul of a Demon. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iTrollSoul}{
	\s\MYname {Soul of a Troll}
	\s\MYnumber {}
	\s\MYtext {The soul of a Troll. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iFaeSoul}{
	\s\MYname {Soul of a Fae}
	\s\MYnumber {}
	\s\MYtext {The soul of a Fae. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iMinotaurSoul}{
	\s\MYname {Soul of a Minotaur}
	\s\MYnumber {}
	\s\MYtext {The soul of a Minotaur. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iGoblinSoul}{
	\s\MYname {Soul of a Goblin}
	\s\MYnumber {}
	\s\MYtext {The soul of a Goblin. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iBasiliskSoul}{
	\s\MYname {Soul of a Basilisk}
	\s\MYnumber {}
	\s\MYtext {The soul of a Basilisk. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iEntSoul}{
	\s\MYname {Soul of a Ent}
	\s\MYnumber {}
	\s\MYtext {The soul of a Ent. \emph{This item is incorporeal. It cannot be found by normal search mechanics and can only be traded away via a mechanic that interacts with ``Soul'' items.}}
}

\NEW{Item}{\iNecklace}{
	\s\MYname {A Shiny Necklace}
	\s\MYnumber {}
	\s\MYtext {A shiny necklace of emeralds and fine gold filigree.}
}