%%%%%
%%
%% This file sets up the Sign and Label datatypes and creates Sign and
%% Label macros.
%%
%% Signs generally represent interesting parts of game area, usually
%% as things posted on walls.  Labels represent other things, often on
%% or inside envelopes, that are part of complex mechanics.
%%
%% The default value for \MYloc will inherit location from the Place
%% or Sign most immediately up the ownership tree.  Override this by
%% setting \MYloc to anything (even blank).
%%
%% Sign is for full-sized signs that would cover most of a large
%% manila envelope; SignMedium is for signs sized to half-sized manila
%% envelopes; SignSmall is for signs sized for small manila envelopes
%% (the same size as item cards).  Label, LabelMedium, and LabelSmall
%% are analagous, but they don't have a \takedownby note at the
%% bottom.  You can always use a sign or label without an envelope or
%% with a differently-sized envelope.  Choose which based on
%% visibility and content.
%%
%% SignTiny is for signs you want to be hard to find; it is small and
%% does not have a \takedownby note.  SignDot is for a very small
%% "dot" which only has a title.
%%
%% SignStrip produces a strip of paper (without a \takedownby note)
%% with labels on the outside that show on both sides if you fold it
%% in half.  These are a convenient alternative to sub-envelopes. They
%% can also be used for "s-packets" taped to walls (see
%% Extras/README-s-packets).
%%
%% LabelCover produces a label similar to the cover to a research
%% notebook.  LabelPage, likewise, produces a page.
%%
%% EOG is for full-sized end-of-game signs.
%%
%%%%%

\DECLARESUBTYPE{Sign}{Element}
\PRESETS{Sign}{
  \FD\MYloc	{\mylocation} %% real-space location
  \FD\MYtext	{} %% text of sign
  }
\POSTSETS{Sign}{
  \edef\mylocation{\MYloc}
  \protected@edef\@ownerstring{%
    \MYname%
    \ifx\mylocation\empty\else\ (\mylocation)\fi%
    }
  }
\def\mylocation{}

\def\loc 1{\rs\MYloc{ 1}}

\DECLARESUBTYPE{SignMedium}{Sign}
\DECLARESUBTYPE{SignSmall}{Sign}
\DECLARESUBTYPE{SignTiny}{Sign}
\DECLARESUBTYPE{SignDot}{Sign}
\PRESETS{SignDot}{\s\MYtext{}}

\DECLARESUBTYPE{Label}{Sign}
\PRESETS{Label}{\s\MYloc{}}
\DECLARESUBTYPE{LabelMedium}{Label}
\DECLARESUBTYPE{LabelSmall}{Label}

\DECLARESUBTYPE{SignStrip}{Sign}
\DECLARESUBTYPE{LabelCover}{Label}
\DECLARESUBTYPE{LabelPage}{Label}

\DECLARESUBTYPE{EOG}{Sign}
\PRESETS{EOG}{%
  \s\MYname	{End Of Game}
  \s\MYtext	{{\bf\Huge You may not pass through here.}}
  }


%%%%%
%% \signbig[<location>]{<name>}{<text>}
%% \eog[<location>]
%%
%% \signmdeium[<location>]{<name>}{<text>}
%% \signsmall[<location>]{<name>}{<text>}
%% \signtiny[<location>]{<name>}{<text>}
%% \signdot[<location>]{<name>}
%%
%% \labelbig{<name>}{<text>}
%% \labelmedium{<name>}{<text>}
%% \labelsmall{<name>}{<text>}
%%
%% \signstrip[<location>]{<name>}{<text>}
%% \labelcover{<name>}{<text>}
%% \labelpage{<name>}{<text>}
\newinstance{Sign}{\signbig[3][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}\s\MYtext{ 3}}
\newinstance{EOG}{\eog[1][\mylocation]}{\s\MYloc{ 1}}

\newinstance{SignMedium}{\signmedium[3][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}\s\MYtext{ 3}}
\newinstance{SignSmall}{\signsmall[3][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}\s\MYtext{ 3}}
\newinstance{SignTiny}{\signtiny[3][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}\s\MYtext{ 3}}
\newinstance{SignDot}{\signdot[2][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}}

\newinstance{Label}{\labelbig[2]}{
  \s\MYname{ 1}\s\MYtext{ 2}}
\newinstance{LabelMedium}{\labelmedium[2]}{
  \s\MYname{ 1}\s\MYtext{ 2}}
\newinstance{LabelSmall}{\labelsmall[2]}{
  \s\MYname{ 1}\s\MYtext{ 2}}

\newinstance{SignStrip}{\signstrip[3][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}\s\MYtext{ 3}}
\newinstance{LabelCover}{\labelcover[2]}{
  \s\MYname{ 1}\s\MYtext{ 2}}
\newinstance{LabelPage}{\labelpage[2]}{
  \s\MYname{ 1}\s\MYtext{ 2}}


%%%%%
%% \sEOG{}
%% use \sEOg[\loc{<location>}]{} for EOG sign at a specific place
\NEW{EOG}{\sEOG}{
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Sign}{\sTest}{
  \s\MYname	{A Room}
  \s\MYloc	{10-250}
  \s\MYtext	{A lecture hall with large, sliding blackboards.}
  }
\NEW{Sign}{\sOnyx}{
	\s\MYname {A Portrait}
	\s\MYtext {A portrait of the Onyx dragon, in his younger days.}
}
\NEW{Sign}{\sWard}{
	\s\MYname {A Ward}
	\s\MYtext {This ward glows with protective energy}
}
\NEW{Sign}{\sDisabledWard}{
	\s\MYname {Disabled Ward}
	\s\MYtext {This ward no longer glows, stripped of all protective abilities}
}
\NEW{Sign}{\sTelerune}{
	\s\MYname {Teleportation Rune}
	\s\MYtext {This is the teleportation rune you arrived on. It glows with arcane energy.}
	}
\NEW{Sign}{\sBrokeTelerune}{
	\s\MYname {Broken Teleportation Rune}
	\s\MYtext {This is the teleportation rune you arrived on. It is quite clearly broken.}
	}
\NEW{Sign}{\sWindyCorridor}{
  \s\MYname	{A Windy Corridor}
  \s\MYtext	{This corridor leads outside where messengers are waiting for each army. You can use this corridor to dispatch missives to your army, leading them to war or to seek peace with the humans.}
  \s\MYitems	{\multi{20}{\iMissive{}}}
  }
\NEW{Sign}{\sDSignA}{
	\s\MYname {Sign 1}
	\s\MYtext {You arrive at the bottom of the steps and see a 30x30 square foot area, dimly lit by torches, ahead of you. The walls are made of solid stone, and after some exploring you find three paths.


If you take the left path, go to {\bf sign 2}.



If you take the middle path, go to {\bf sign 8}.



If you take the right path, go to {\bf sign 14}.



Or, you may go back up the stairs and {\bf exit the dungeon}}
	\s\MYitems {\multi{5}{\iTorch{}}}
}
	
\NEW{Sign}{\sDSignB}{
	\s\MYname {Sign 2}
	\s\MYtext {After a brief journey down the path, you come to a wide, rushing, river. 
	
	If you have the ability ``fly''ù or have a \iRope{}, you can pass over the river. If you use the rope, tear up the card and write ``Bridged''ù on this sign. If you wish to destroy the bridge, spend 5 mins touching this sign and cross out the word ``Bridged.''ù If you pass over the river, go to {\bf sign 3}.
	
Alternatively, if you would like to explore the river, turn to {\bf sign 19}.}
	\s\MYitems {}
	}
	
\NEW{Sign}{\sDSignC}{
	\s\MYname {Sign 3}
	\s\MYtext {After passing the river, you come to a large cavern. It is pitch black. 
	
	If you do not have an item or ability that provides light, you cannot pass. If you \emph{can} pass, turn to {\bf sign 4}.

	If you \emph{cannot} pass, return to {\bf sign 2}.}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignD}{
	\s\MYname {Sign 4}
	\s\MYtext {You come to a room filled with enormous stalagmites and stalactites. 
	
	If there are {\bf three or more} people in the group, everyone must resist a wound 10 attack. 
	
	If you wish to run though a side passage and not venture deeper proceed to {\bf sign 6}. 
	
	If you wish to venture deeper, then everyone with CR greater than 5 takes a -5 CR penalty for 30 minutes or until exiting the dungeon, from the pointy stalactites. Turn to {\bf sign 5}.}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignE}{
	\s\MYname {Sign 5}
	\s\MYtext {You come to a grand doorway. Power emanates from behind it. There is a ward on the wall next to the door. You cannot pass unless the ward is broken, or if you know otherwise. 


	If you can pass, and choose to do so, proceed to {\bf sign 7}. You may also retreat back to {\bf sign  3}.
	
	\emph{If you have a mechanic that allows you to break or repair wards, you may change the status of this ward by fulfilling the requirements of the mechanic, then crossing out the previous status and writing in the new one below. Tell a GM if you change the status of the Ward.}\\
	\LARGE{Ward Status: Active}

	}
	\s\MYitems {}
	%\s\MYsigns {\sWard{} \sDisabledWard{}}
	}
	\NEW{Sign}{\sDSignF}{
	\s\MYname {Sign 6}
	\s\MYtext {{\bf Tell a GM immediately if you enter this room.} Your noise and movements have awoken a foul Krogoth! Huge jets of flame fly from its granite carapace as its hideous eyes turn to look at you. 
	
	If your group's CR is more than 45, take an item from the pouch and turn to {\bf sign 5}.  
	
	Otherwise, you must flee to {\bf sign 20}.}
	\s\MYitems {\iPhylactery{}}
	}
	\NEW{Sign}{\sDSignG}{
	\s\MYname {Sign 7}
	\s\MYtext { {\bf The Ritual Chamber}

This chamber, cut from the heartstone of the mountain itself, is awash in raw power. A raised dais holds a pedestal, with an indentation that perfectly fits an idol. Incense holders burn along all sides of the chamber. 

You may go back to {\bf sign 5}.}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignH}{
	\s\MYname {Sign 8}
	\s\MYtext {After a journey down a twisting corridor, you arrive at a bridge, guarded by the Gatekeeper, an ancient troll. If your party does not include a Troll, you must each pay the troll's toll of one item each. Place an item in the pouch attached to this sign. If the group chooses to fight the troll, you must make a combined CR attack of greater than 20. Even if the troll is a member of your party, you \emph{may} attack the Gatekeeper. 
	
	If you fail, you are all knocked out. Return immediately to {\bf Sign 1} and regain consciousness.
	
	If you succeed in your attack, you may each take an item from the troll's pouch - the packet attached to this sign. 
	
	If you pass (regardless of if you successfully attack the Gatekeeper), turn to {\bf Sign 9}. 
	
	You may dive into the water under the bridge instead if you like, if you do, turn to {\bf sign 19}.

You may also exit to {\bf sign 1} without paying the toll.}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignI}{
	\s\MYname {Sign 9}
	\s\MYtext {After passing over the bridge, you find a cave filled with large crystals. You may explore this cave, or journey through it 
	
	If you pass through immediately, without exploring, to {\bf sign 10}. 
	
	If you explore this cave, turn to {\bf sign 21}.

	You may also exit to {\bf sign 8.}}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignJ}{
	\s\MYname {Sign 10}
	\s\MYtext {You find yourself in a large mushroom forest. Fungi grow all over the walls and ceiling of this room. If you want, you may pick a mushroom by taking an item from this pouch. 
	
	If you do, turn to {\bf sign 11}. 
	
	Otherwise, turn to {\bf sign 12}.

	You may also exit to {\bf sign 9}.}
	\s\MYitems {{\multi{20}{\iCFungus{}}} }
	}
	\NEW{Sign}{\sDSignK}{
	\s\MYname {Sign 11}
	\s\MYtext {The walls come alive! If you have a fire attack or 3 sources of light, you may drive back the animated fungi.
	
	If you succeed in fighting off the fungi, proceed to {\bf sign 12}. 
	
	Otherwise, flee to {\bf sign 15}.}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignL}{
	\s\MYname {Sign 12}
	\s\MYtext {You come to a great bronze door set deep into the surrounding stone. 
	
	If your group's CR is 25 or more, you may force open the door and proceed to {\bf sign 13}. 
	
	If not, you must exit to {\bf sign 10}.}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignM}{
	\s\MYname {Sign 13}
	\s\MYtext {You find a small rock hewn room with what appears to be a piece of a broken sword. If you pick it up, take the item from the attached packet.

Exit to {\bf sign 10.}}
	\s\MYitems {\iVorpalSwordofWonder{}}
	}
	\NEW{Sign}{\sDSignN}{
	\s\MYname {Sign 14}
	\s\MYtext {On the other side of the doorway, you find a fountain, bubbling up from the depths of the earth into a marble basin. You may drink from the fountain.
	
	If you do, turn to {\bf sign 23} 
	
	If you choose not to, you may turn left and proceed to {\bf sign 15}. 
	
	You may also turn right and proceed to {\bf sign 10}.}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignO}{
	\s\MYname {Sign 15}
	\s\MYtext {You come across the lair of a massive spider! 
	
	If your group CR is greater than 25 or 5 or less, turn to {\bf sign 16}. 
	
	Otherwise, flee back to {\bf sign 14}. You are now poisoned you must spend 5 minutes pretending to be violently ill (this effect goes away if you exit the dungeon).}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignP}{
	\s\MYname {Sign 16}
	\s\MYtext {You find a massive underground lake being fed by a mighty river. 
	
	You may turn left and proceed to {\bf sign 4}.
	
	You may turn right and proceed to {\bf sign 17}. 

	You may also exit to {\bf sign 14}.}
	\s\MYitems {}
	}
	
	\NEW{Sign}{\sDSignQ}{
	\s\MYname {Sign 17}
	\s\MYtext {After some journeying, you enter an armory. There are wands, weapons, and some daggers here.  Two in particular stand out. One is \iRitualWand{} -- there is no mistaking it's aura. The other is a dagger made of some dark metal you don't recognize, with a twisted blade. It is marked with the symbol of the God of War. You may take an item from the pouch if you desire, with one exception. The \iDagger{} cannot be touched unless you know otherwise. 
	
	You may proceed onward to {\bf sign 18}. 
	
	You may also return to {\bf sign 16}.}
	\s\MYitems {\iRitualWand{} \iDagger{} \iStorch{}}
	}
	\NEW{Sign}{\sDSignR}{
	\s\MYname {Sign 18}
	\s\MYtext {You enter a large chamber filled with many treasures, including a holy book that seems to draw your eye. The cover is emblazoned with the symbol of the God of War. You may only take the book if you know you can, otherwise a mysterious force prevents you from touching the book. If you can touch the book, take an item from the pouch.

You may exit to {\bf sign 17}.}
	\s\MYitems {\iHolyBook{}}
	}
	\NEW{Sign}{\sDSignS}{
	\s\MYname {Sign 19}
	\s\MYtext {You dive into the dark, icy waters. 
	
	If your group CR is more than 15, you succeed in finding an item in the river bed. Take an item from the pouch and turn to {\bf sign 22}. 
	
	If your group CR is less than 15, take -5 CR penalty for 30 mins or until you exit the dungeon as you are battered by the rapid waters. Turn to {\bf sign 16}.}
	\s\MYitems {\iLovePotion{} {\multi{10}{\iGingko{}}}}
	}
	\NEW{Sign}{\sDSignT}{
	\s\MYname {Sign 20}
	\s\MYtext {In the midst of fleeing from the monster, you find yourself atop a large waterfall. 
	
	A luminous white glow from an island in the middle of the rushing river catches your attention. If you choose to jump to the island, turn to {\bf sign 24}.
	
	Otherwise, your only option is to jump off the waterfall! Turn to {\bf sign 19.}}
	\s\MYitems {}
	}

	\NEW{Sign}{\sDSignU}{
	\s\MYname {Sign 21}
	\s\MYtext {The crystals in their shimmering light seem to move menacingly. At a second glance, they are moving menacingly! You are fighting a crystal golem! 
	
	If your party's CR is greater than 20, you may fight the golem off and turn to {\bf sign 12}. 
	
	Otherwise, you must flee to {\bf sign 20}. As you flee, the golem's parting shot embeds a crystal in your body. Take a CR penalty of -5 for 30 minutes, or until you exit the dungeon. You must pretend to have a wounded arm or leg (your choice).}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignV}{
	\s\MYname {Sign 22}
	\s\MYtext {After braving the river, you reach the other side. You find two paths, one leading north and one leading south. There is a fish that leaps from the river and says cryptically: 	``The Darkness Stirs''.	It plops back in the water and make no splash. 
	
	If you take the south path, turn to {\bf sign 16}. 
	
	If you take the north path, turn to {\bf sign 4}.}
	\s\MYitems {}
	}
	\NEW{Sign}{\sDSignW}{
	\s\MYname {Sign 23}
	\s\MYtext {After drinking the water, you feel reinvigorated. Gain5 CR for the next 30 mins (this buff remains even if you exit the dungeon for the full 30 minutes. However, the doors on either side of the room have sealed themselves shut. \emph{You may only drink from the fountain during per game}. 
	
	You must exit to {\bf sign 1.}}
	\s\MYitems {}
	}
	
	\NEW{Sign}{\sDSignX}{
	\s\MYname {Sign 24}
	\s\MYtext {You jump to the island perched on the edge of an underground waterfall. It was a farther jump than you thought, and you almost slip an fall into the rushing river. In front of you, on a hastily erected pedestal is an orb no bigger than a pearl. From it emanates a powerful light.
	
	A powerful force protects the object, preventing it from being removed, however, you think you might be able to destroy it.
	
\begin{itemize}
	\item If no more than 1 hr has elapsed since game began, you may make a CR attack greater than 50 against the object to break it.
	\item If between 1 and 2 hours have elapsed since game began, you may make a CR attack greater than 40 against the object to break it.
	\item	If between 2 and 3 hours have elapsed since game began, you may make a CR attack greater than 30 against the object to break it.
	\item	If it is the last hour of game (between 3 and 4 hours elapsed since game start), you may make a CR attack greater than 20 against the object to break it.
\end{itemize} 
	If you choose to attack the orb and succeed in destroying it, \emph{tell a GM, asap}.
	
	The only way off the island is to leap off, into the waterfall. Turn to {\bf sign 19}.}
	\s\MYitems {}
	}
	
	\NEW{Sign}{\sCauldron}{
		\s\MYname {Cauldron}
		\s\MYtext {This is a massive Cauldron, used to brew potions and tea.}
		}
	\NEW{Sign}{\sLock}{
		\s\MYname {Door to Treasure Room}
		\s\MYtext {This is a solid stone door with a keyhole. You may only pass if you have an item that tells you that you may do so.
		If you do not have any such item, you may enter this room if you get a level 4 hand in decking. If anyone asks you what you are doing, you must tell them that you are trying to pick the lock to the room.}
		}
		
\NEW{Sign}{\sGarden}{
	\s\MYname {Garden}
	\s\MYtext { This is the Garden. It is a verdant area in contrast to the drab stone construction of the rest of the castle. Birds are chirping, plants are growing, and a decorative fountain sits in the middle.}
	}
	\NEW{Sign}{\sFountain}{
		\s\MYname {Decorative Fountain}
		\s\MYtext {This is a decorative marble fountain of a fierce dragon. Water flows from its mouth}
		}
\NEW{Sign}{\sMeadow}{
	\s\MYname {Meadow}
	\s\MYtext {There are many different plants growing in this meadow. If you spend one minute touching this sign, you may take an item from the pouch.}
	}
	
\NEW{Sign}{\sKitchen}{
	\s\MYname {Kitchen}
	\s\MYtext {This is the kitchen for the castle. In one corner there is a large cauldron. In another there is a larder.}
	}
	
\NEW{Sign}{\sLarder}{
	\s\MYname {Larder}
	\s\MYtext {This is the larder for the kitchen. In addition to massive amounts of food, it contains some herbs and other supplies. If you spend 1 minute touching this sign, you may take an item from the pouch.}
	}
	
\NEW{Sign}{\sLibrary}{
	\s\MYname {Library}
	\s\MYtext {This is the castle's library. Rows of books line the walls, with candles providing illumination.}
	}
\NEW{Sign}{\sBookshelf}{
	\s\MYname {Bookshelf}
	\s\MYtext {One of the numerous bookshelves that line the library. If you have a mechanic that deals with research in the library, do that here.}
	}
	
\NEW{Sign}{\sIdolShelf}{
	\s\MYname {Shelf}
	\s\MYtext {This shelf has three curious idols on it. They almost glow with magical power. Spend one minute touching this sign to take one of the idols from the shelf}
	}
	
\NEW{Sign}{\sTRoom}{
	\s\MYname {Onyx's Treasure Room}
	\s\MYtext {This is the treasure room of the Onyx Dragon. Massive piles of gold overflow onto the floor, studded with all kinds of precious gems. There is a shelf with magical artifacts upon it. If you spend one minute touching this sign, you may take an item from the pouch.}
	}
	
\NEW{Sign}{\sTeleporter}{
	\s\MYname {Teleport Room}
	\s\MYtext {This is the teleporter room that you arrived in at the beginning of the meeting. You can exit here if there are less than 30 minutes to game end, as long as the Teleporter Rune is functioning. {\bf If you choose to do so, you will not be able to return.} Touch this sign for 2 minutes  to leave the game. {\bf This action is interruptible.}}
	}
	
\NEW{Sign}{\sGolemLab}{
	\s\MYname {Golem Lab}
	\s\MYtext {This is the golem lab. There are gears, stone, and metals in various piles around the room.}
	}
	
\NEW{Sign}{\sDiningRoom}{
	\s\MYname {Dining Room}
	\s\MYtext {This is a massive banquet hall. Rows of candles light the tables, and torches line the walls.}
	}
	
\NEW{Sign}{\sVotingChamber}{
	\s\MYname {Voting Chamber}
	\s\MYtext {This is a chamber used for holding meetings. There are rows of desks, and a podium at the head of the chamber. There is a magical board, denoting the troop movements of the armies of the representatives.}
	}
	
\NEW{Sign}{\sPodium}{
	\s\MYname {Podium}
	\s\MYtext {This is a podium in the Voting Chamber.}
	}
\NEW{Sign}{\sBoard}{
	\s\MYname {Army Board}
	\s\MYtext {This is a magical board that lists every army that has deployed. If a delegate votes to send their army, the army will be added to the board.}
	}
\NEW{Sign}{\sDungeonEntrance}{
	\s\MYname {Dungeon}
	\s\MYtext {This is the Dungeon. It is dark and dank. You must read the greensheet before entering.}
	}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
