\documentclass[green]{guildcamp2}
\begin{document}
\name{\gBattleReference{}}

Reference for when players come ask you for things:

-- Any player who carries a Tear of Magic gets +5CR while doing so. They lose this ability if they lose the tear.

-- Success at the God of War ritual summons the NPC Groznak.

This greensheet is a GM-only reference for the battle mechanics, as well as an end-of-game reference.

Human army strength is 3d4 + 3

Monster army strength is:

Each committed monster army adds 1

-- Ezekiel +1: This is the Fae leader, who sits on top of an existing character. At game wrapup, ask the player representing Ezekiel if he wishes to participate in the battle. If so, Monster army strength gets +1. The player does not necessarially have to have their armies commit.

-- Human poisoning ritual: +2

-- Human enslavement ritual: +1

-- Humans to trees ritual: +1

-- Golem Army: +1 (this army must be deployed using the Golem control rod.  Turns out he has an army of golems in the basement)

-- Goblin’s orb: +1 (if, at the end of the game, the player wielding this orb has their armies commit, their army gets +1 strength)

There is a location/sign titled ``A windy cavern''. This is in an out-of-the-way place (the end of the really long corridor). This has a set of forms that have a check-box for either going to war or peace, and a field for what army is being represented. We need to tell people that they cannot fake being from another army unless they know otherwise. This ballot is not an in-game item and you cannot interact with it unless you know otherwise (only the wizard can do so.) The wizard can annotate it as follows:

Triangle: Wizard thinks this army is dangerous and should be killed. +1 on the ``sue for peace'' die roll

Circle: Wizard thinks the army is good and shouldn't be killed. -1 on the ``sue for peace'' die roll

By default players have a 2/6 chance of successfully suing for peace.

GMs should periodically check the ballot box. When decisions are made, annotations like the following should be written up on the ``Army board'' in the main room, which has columns for ``Army'' and ``Latest Status Report''

Nothing: ``Idle''

War: ``On the march''

Peace: ``Scout has not yet returned''

Some characters have non-traditional deployments:

Wizard: ``There is a stirring in the astral plane...'' (this is just a trick he's doing to make it seem like something is happening)

Demon: ``There is a stirring in the astral plane...'' (the demons aren't going to show up until the end of the battle)

Cleric: Ogres remain Idle.

The demon can kill the scouts to stir up a bit of chaos. This will cause an army to appear as if it might have sued for peace (``Scout has not yet returned''), but it will go back to its previous state after 10 minutes or so.

For Minotaur: When Sphinx has been trapped. Notify sphinx that they cannot leave the maze until it is complete and that they have a -5CR until they exit.

\end{document}
