\documentclass[green]{guildcamp2}
\begin{document}
\name{\gBattle{}}

The humans are massing to invade the monster's territory. \cOnyx{} has called his greatest strategists together to assess the human forces and what forces the monsters can muster to counter them. At present, no monster armies have been deployed, but characters may deploy their army during the course of play. Once a player has committed their forces to the monster army, they are fully deployed and cannot be revoked unless you know otherwise. A player's death will not affect the status of their army's deployment.

The battle will all come down to the relative strength of the monster and human armies.

The monster army strength will be equal to the number of armies deployed (unless you know otherwise, all of the character's armies are of equal strength). There may be modifiers in the game that further strengthen either the monster or human armies and tip the balance of power. If you are uncertain whether a given item or event is significant enough to sway the final battle, ask a GM.

\cOnyx{}'s scouts report that, like the monster army, the humans are discussing over exactly which forces to mobilize and where to mobilize them. They estimate that the humans can muster 3d4 + 3 armies (3d4 is the sum of three rolls of a 4-sided dice). Like the monster armies, the exact deployments of the human army won't be known until all monster deployments are completed, but there may be scout reports who provide updates on the status of both the monster and human deployment.

If the humans and monsters deploy the same number of armies, a massive bloodshed will ensue with no clear victor. If the monsters deploy at least 2 more armies than the humans, the humans will be routed and the monsters will continue to push into the human territory. If the humans deploy at least 2 more than the monsters, the monsters will be crushed and their territories will be extremely vulnerable to the human invaders.

To commit your forces to the combined monster army, head to the end of the windy cavern. There you can connect with your messengers to send missives to your forces to deploy. These missives are not in-game items, but you can head down the windy cavern with other players if you wish to do so and show them the missive. \textbf{You cannot impersonate another army unless you know otherwise.}

The \cSphinx{} is an individual and does not represent an army, but is powerful enough to count as an army in its own right. It does not have to choose to join the monster army until the battle has begun.

It is also possible to send a missive telling your forces to flee the monster's battle and seek asylum with the humans. You believe this can be done with some degree of secrecy. However, there is a one-in-three chance that the humans will interpret your maneuver as a hostile action and attempt to wipe your army out. There may be modifiers which improve your odds of successfully negotiating with the humans.

The Supreme Leader is the head general in charge of deploying the monster armies against the human incursion. An extremely talented leader may be able to improve the monster army strength.

\end{document}
