\documentclass[green]{guildcamp2}
\begin{document}
\name{\gGolem{}}

After examining the golem laboratory of the great (and long dead) gnomish artificer Zumwalt, you believe you have managed to work out how to reproduce her work and build a golem of your own. There are enough parts here for exactly one golem, but you will need Zumwalt's notes to put it all together and make it work. The golem is also keyed to Zumwalt's voice, but luckily you have deduced that Zumwalt left an alternative way to command her constructs: anyone who holds Zumwalt's control rod (\iGolemControlRod{}) can command her golems.

To build a golem, you will first need to find all of Zumwalt's notes. It seems as if Zumwalt was experimenting with a bizarre piece of technology known as a \emph{printing press} and has many copies of her journal. You will need to find a complete copy of each section to begin construction:

\begin{enum}[Requirements]
	\item \iGolemNotesA{}
	\item \iGolemNotesB{}
	\item \iGolemNotesC{}
	\item \iGolemNotesD{}
	\item \iGolemNotesE{}
	\item A deck of cards
\end{enum}

Once you have the parts, gather at least three members interested in constructing a golem into the golem laboratory. Place all the golem notes on the table in front of everyone and verify that all five parts are present. Then at least two players must get a level 3 hand in decking. While doing so, discuss the intricacies of golem construction and your plans for the golem.

Upon completing the ritual the golem is constructed, but inactive. Find a GM before proceeding further.

To activate the golem, you must possess  \iGolemControlRod{} and point it at the golem, while all members incant ``Expergiscendum'' five times.

After this point, anyone with the control rod may order the golem around. It moves slowly but is extremely powerful. You may also dispatch the golem to join either the monster or human army by traveling with it (and its control rod) to the end of The Windy Corridor. Write a missive on the sheet at the end of the corridor, as if you were commanding an army; the golem will head out immediately and cannot be recalled.

\end{document}
