\documentclass[green]{guildcamp2}
\begin{document}
\name{\gsphinxriddles{}}

\section{Riddles}
You have selected these riddles to as the creatures here! You have selected some to challenge while others are intended for a more relaxed experience. You, of course, are known for making up riddles on the spot. These riddles are not in order.

\begin{enum}
	\item I appear once every ``day'', twice each ``year'', but thrice in ``an era.'' What am I?
	
	\item A tall green hat sits atop my head, I'm always wearing my coat of red, I'm not always alone. What am I?
	
	\item My presence is but once a day, my embrace is searing, my smile is beaming. What am I?
	
	\item Dark is my skin, but of course I bleed red! Green daggers protect my sweet surprise. What am I?
	
	\item What is the unique characteristic of the following words: coughing, thirsty, defiant?
	
	\item Cut into me, write in me, use me for shelter, use me to calculate, burn me. What am I?
	
	\item If you throw me from the window, I will leave a grieving wife. Bring me back, but in the door, and you'll see someone giving life! What am I?
	
	\item I rise before I am born, I shrink before I am gone. I am the greatest thing since the beginning of time! What am I?
	
	\item Voiceless I cry, wingless I flutter. Toothless I bite, mouthless I mutter. What am I?
	
	\item The wind blows my hat away, my dress is ever slipping. I often perch on a special throne made for me. At my liveliest you can see me fade! What am I?
	
	\item I have street but no pavement. I have cities but no buildings. I have forests but no trees. I have rivers yet no water. What am I?
	
	\item Only you can see me, examine me while you sleep, my hair stands up and deflects attacks to the prismatic egg with a flower inside! What am I?
	
	\item What word can be written forward, backward, or upside down and can still be read from left to right?
	
	\item I spend my life keeping pigs warm, I travel so much I usually need stiches, and I am forever searching for my long lost love. What am I?
	
	\item I look at you, you look at me. I raise my right, you raise your left. What am I?
	
	\item My owner can's see me, though I protect the greatest treasure he or she posesses! Sometimes I wear a coat. Sometimes I wear a tail. Often I go naked. What am I?
	
	\item What belongs to you but is something that others use more than you?
	
	\item Twice ten are six of us. Six are but three of us, Nine are but four of us. Twelve are but six of us. Five are but four of us. Who are we?
	
	\item Many have heard it, but nobody has ever seen it, and it will not speak back until spoken to. What is it?
	
	\item When can you add two to eleven and get one as the correct answer?
	
	\item Pronounced as one letter; written with three. Two letters are there and only two in me. I'm double; I'm single. I'm black, blue, and gray. I'm read from both ends and the same either way. What am I?
	
	\item Can you name four days that start witht he letter ``T''?
	
	\item One day Alice meets the Lion and the Unicorn in the Forest of Forgetfulness. She knows that the Lion lies on Sundays, Tuesdays, and Wednesdays but tells the truth on the other days of the week. The Unicorn, on the other hand, lies on Thursdays, Fridays, and Saturdays, but tells the truth on the other days of the week. Now they make the following statements to Alice:
The Lion says, ``Yesterday was one of my lying days.''
The Unicorn says, ``Yesterday was one of my lying days, too.''
What day is it today?

	\item Here are three answers: the first answer is Answer A. The second answer is Answer A or B. The third answer is Answer B or C. There is only correct answer. Which is it?
	
	\item Name a word in the Human English dictionary which has a silent ``Z''.
	
	\item I never was there, I am always to be. You have never seen me, nor will you. Nevertheless, I am the confidence of everyone. What am I?
	
	\item Look at me. I can bring a smile to your face, a tear to you eye, or even a thought to your mind. But, I cannot be seen. What am I?
\end{enum}

\begin{enum}[Directions]
	\item Ask as many riddles as possible during your time at this event.
	\item Ask a riddle to each other creature at this event. Ten or more correct answers means that the monsters have won your vote! (Add your own riddles to this list if you wish, these are only here to help if you get stuck.)
	\end{enum}

\section{Answers}
\begin{enum}
\item vowels
\item cherries
\item the sun
\item blackberries
\item they each have three letters that are in alphabetical sequence
\item log
\item the letter ``N''
\item bread
\item the wind (from The Hobbit)
\item a candle
\item a map
\item the back of your eyelid
\item ``NOON''
\item socks
\item a mirror
\item the back of your head
\item your name
\item letters
\item and echo
\item eleven o'clock. add two hours and it is one o'clock
\item ``EYE''
\item Tuesday, Thursday, Today, Tomorrow
\item Today is Thursday because the lion's statement can only be true on Thursdays and Mondays. The Unicorn shares no lying days with the lion so it must be lying.
\item the correct answer is the third answer. B or C is the only option that allows for only one of the three to be true.
\item rendezvous
\item the future
\item the past
\end{enum}

\end{document}
